---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2022-10-120'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4,nnet,rstan,brms)
knitr::opts_knit$set(root.dir = here()) # set root fot the whole file
refit=T
```

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.

```{r}
social_data <-  read_csv(file = paste0("./data/social/data_social_all_participants.csv"))
social_data<-social_data%>%mutate(player=ifelse(group=="adults",player,player+1000))

## get unreasonable nans
nans<-social_data%>%
  filter(is.na(demo_type) | is.na(cells))%>%pull(player)%>%unique()

social_data<-social_data%>%filter(!(player %in% nans))
R_subj=social_data%>%group_by(player)%>%summarise(n_r=length(unique(round)))%>%pull(n_r)


social_data<-social_data%>%#drop_na()
  filter(!is.na(demo_type) & !is.na(cells))%>%#filter(player<30)%>%# get a sub-sample of both adults and adolescents 
  mutate(soctype=case_when(
    demo_type=="gem_found"~3,# i need that to index the different social weight parameters
    demo_type=="gem_not_found" | demo_type=="no_gem"~2,
    str_detect(demo_type,"never_exploit") ~ 1
  )
  )
#give kids a unqiquely numbered indx
social_data<-social_data%>%mutate(player=ifelse(group=="adults",player,player+1000))
R_subj=social_data%>%group_by(player)%>%summarise(n_r=length(unique(round)))%>%pull(n_r)
#keep<-unique(social_data$player)[R_subj==12]# keep only participants who completed all trials

hist(social_data$round)
#only keep comsocial_dataplete rounds
#social_data<-social_data%>%filter(player %in% keep)
```

# Fit model to social data

There is a credible interaction between SI use and agegroup. 

TODO: is there something wrong here? Is copy calculated correctly?
```{r}
social_data%>%group_by(demo_type,player,round,group,gem_found,soctype)%>%
  filter(!is.na(social_info_use))%>%filter(social_info_use=="copy")%>%count(social_info_use)%>%
  ggplot(aes(x=soctype,y=n,color=group))+
  geom_point(alpha=0.2,position=position_dodge(0.9))+
  stat_summary(position=position_dodge(0.9),size=1)+
  geom_hline(yintercept = 25/64,linetype="dotted",color="red")+
  scale_x_continuous(name="Social info quality",breaks=c(1,2,3),labels=c("Bad","Medium","Good"))+
  scale_y_continuous(name="Number of copying decisions per trial")+
  theme_bw(15)+
  #facet_wrap(.~gem_found,labeller = label_both)+
  theme(axis.text.x =element_text(angle=45,hjust=1))

ggsave(filename = "copying_choices.png")
# poisson regression for group effects

p_model<-social_data%>%group_by(demo_quality,player,round,group,demo_type)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(social_info_use=="copy")%>%
  glmer(n~group*demo_quality+round+(1|player),data=.,family="poisson")#%>%summary()

p_model%>%summary()

vec<-c("Adults","Medium SI","Bad SI","Adults x Medium SI","Adults x Bad SI")
vec_2<-vec[c(5,4,3,2,1)]

model_plot<-sjPlot::plot_model(p_model)+
  theme_bw(14)+
  ggtitle("")+
  scale_x_discrete(labels=vec_2)

sjPlot::plot_model(p_model, type = "pred",terms = c("demo_quality", "group"))

ggsave(model_plot,file = "./plots/poisson_regression.png",width=4,height=4)
```

# Fit model

prepare data to be passed to stan.

```{r}
# first: cheat and take out "incomplete" cases
social_data_forfit<-social_data%>%filter(group=="adolescents")
R_subj<-social_data_forfit%>%group_by(player)%>%summarise(n_r=list(unique(round)))%>%pull(n_r)#%>%length()

keep_forfit_adolescents<-unique(social_data_forfit$player)#[R_subj==12]# keep only participants who completed all trials
social_data_forfit<-social_data_forfit%>%filter(player %in% keep_forfit_adolescents)

#make it a list of round numbers
# experiment specs
T_max<-25
R_max<-social_data_forfit%>%group_by(player)%>%summarize(env=length(unique(env_number)))%>%pull()%>%max()

social_data_forfit%>%group_by(round,player,)
# number of participants
N<-length(unique(social_data_forfit$player))

#put relevant data into lists
choice = array(-1,c(T_max,R_max,N))
reward = array(-1,c(T_max,R_max,N))
social_info = array(-1,c(T_max,R_max,N))
demo_type_dat = array(-1,c(T_max,R_max,N))
env_rnd = array(-1,c(R_max,N))
gem_found = array(-1,c(T_max,R_max,N))

gem_found_demo_type=array(10,c(T_max,R_max,N))
use_rounds<-rep(-1,N)

for (ppt in 1:N){
  use_rounds[ppt]<-length(R_subj[[ppt]])
  for (r in 1:use_rounds[ppt]){  #loops throug unique round indices per participant
    
    env_rnd[r,ppt]<- social_data_forfit%>%filter(
      round==R_subj[[ppt]][r] ,
      player==keep_forfit_adolescents[ppt]
    )%>%pull(env_number)%>%unique()
    
    for (t in 1:T_max){
      # get choices
      choice[t,r,ppt]<- social_data_forfit%>%filter(
        trial==t ,
        round==R_subj[[ppt]][r] ,
        player==keep_forfit_adolescents[ppt]
      )%>%pull(cells)
      
      # get points
      reward[t,r,ppt]<-  social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adolescents[ppt]
      )%>%pull(points)
      
      #index if gem was found or not
      gem_found[t,r,ppt] <- ifelse(max(reward[1:t,r,ppt])>150,1,2)
      # get demonstrator
      social_info[t,r,ppt]<-social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adolescents[ppt]
      )%>%pull(social_info)
      
      # get demonstrator
      demo_type_dat[t,r,ppt]<-social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adolescents[ppt]
      )%>%pull(soctype)
      
             recoder<-c(4,5,6)

            gem_found_demo_type[t,r,ppt]<-ifelse(gem_found[t,r,ppt]==1,recoder[demo_type_dat[t,r,ppt]],demo_type_dat[t,r,ppt])

    }
  }
}

data_list_adolescents<-list(
  N=N,
  T_max=T_max,
  R_max=R_max,
  R_subj=use_rounds,
  choices=choice,
  rewards=reward,#/80,#just rescaled
  social_info=social_info,
  demo_type=demo_type_dat,
  gem_found=gem_found,
  gem_found_demo_type=gem_found_demo_type,
  env_rnd=env_rnd
)
#its/social_models/all_envs/kalman_ucb_softmax_egreedy/bmt_ucb_fits.csv")
```



# adults model

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.


# Prepare adults data

prepare data to be passed to stan (write to function at some point).

```{r}
# first: cheat and take out "incomplete" cases
social_data_forfit<-social_data%>%filter(group=="adults")
R_subj<-social_data_forfit%>%group_by(player)%>%summarise(n_r=list(unique(round)))%>%pull(n_r)#%>%length()

keep_forfit_adults<-unique(social_data_forfit$player)#[R_subj==12]# keep only participants who completed all trials
social_data_forfit<-social_data_forfit%>%filter(player %in% keep_forfit_adults)
# experiment specs
T_max<-25
R_max<-social_data_forfit%>%group_by(player)%>%summarize(env=length(unique(env_number)))%>%pull()%>%max()
# number of participants
N<-length(unique(social_data_forfit$player))

#put relevant data into lists
choice=array(-1,c(T_max,R_max,N))
reward=array(-1,c(T_max,R_max,N))
social_info=array(-1,c(T_max,R_max,N))
demo_type_dat=array(4,c(T_max,R_max,N))
env_rnd=array(-1,c(R_max,N))
gem_found = array(-1,c(T_max,R_max,N))
gem_found_demo_type=array(10,c(T_max,R_max,N))

use_rounds<-rep(-1,N)

for (ppt in 1:N){
  use_rounds[ppt]<-length(R_subj[[ppt]])
  for (r in 1:use_rounds[ppt]){  #loops throug unique round indices per participant
    
    env_rnd[r,ppt]<- social_data_forfit%>%filter(
      round==R_subj[[ppt]][r] ,
      player==keep_forfit_adults[ppt]
    )%>%pull(env_number)%>%unique()
    
    for (t in 1:T_max){
      # get choices
      choice[t,r,ppt]<- social_data_forfit%>%filter(
        trial==t ,
        round==R_subj[[ppt]][r] ,
        player==keep_forfit_adults[ppt]
      )%>%pull(cells)
      
      # get points
      reward[t,r,ppt]<-  social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adults[ppt]
      )%>%pull(points)
      
      # make index if gem was found already or not
      gem_found[t,r,ppt] <- ifelse(max(reward[1:t,r,ppt])>150,1,2)
      
      # get demonstrator
      social_info[t,r,ppt]<-social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adults[ppt]
      )%>%pull(social_info)
      
      # get demonstrator
      demo_type_dat[t,r,ppt]<-social_data_forfit%>%filter(
        trial==t,
        round==R_subj[[ppt]][r],
        player==keep_forfit_adults[ppt]
      )%>%pull(soctype)
      
      recoder<-c(4,5,6)
      
      gem_found_demo_type[t,r,ppt]<-ifelse(gem_found[t,r,ppt]==1,recoder[demo_type_dat[t,r,ppt]],demo_type_dat[t,r,ppt])
    }
  }
}

data_list_adults<-list(
  N=N,
  T_max=T_max,
  R_max=R_max,
  R_subj=use_rounds,
  choices=choice,
  rewards=reward,#(reward-mean(reward))/sd(reward),#normalize rewards
  social_info=social_info,
  demo_type=demo_type_dat,
  env_rnd=env_rnd,
  gem_found = gem_found,
  gem_found_demo_type=gem_found_demo_type
)
#its/social_models/all_envs/kalman_ucb_softmax_egreedy/bmt_ucb_fits.csv")
```

# Fit stanmodel

```{r}

Q_mod_adol<-stan(
  file="./C_modelfittingCode/stan/model_code/Q_nokeeper_3_2_sw_gem_nogem.stan",
  data=data_list_adolescents,
  pars =c("lr","tau","sw","log_lik"),
  # init=1,
  iter = 1000,
  chains=4,
  cores=4
)

saveRDS(object = Q_mod_adol,file = "./A_GeneratedFiles/modelfits/Q_3_2_sw_gem_nogem_stan_adolescents.rds")
#Q_mod_adol<-readRDS(file = "./A_GeneratedFiles/modelfits/Q_sw_gem_nogem_stan_adolescents.rds")


Q_mod_adul<-stan(
  file="./C_modelfittingCode/stan/model_code/Q_nokeeper_3_2_sw_gem_nogem.stan",
  data=data_list_adults,
  pars =c("lr","tau","sw","log_lik"),
  # init=1,
  iter = 1000,
  chains=4,
  cores=4
)

saveRDS(object = Q_mod_adul,file = "./A_GeneratedFiles/modelfits/Q_3_2_sw_gem_nogem_stan_adults.rds")

```

# did that make any sense
```{r}
# # current benchmark
 Q_mod_adul_2<-readRDS(file = "./A_GeneratedFiles/modelfits/Q_sw_gem_nogem_stan_adults.rds")
# 
# # compare models unsystematically. 
 Q_mod_adul_2_loglik<-loo::extract_log_lik(Q_mod_adul_2)
 Q_mod_adul_loglik<-loo::extract_log_lik(Q_mod_adul)
# # 
# # 
 hist(Q_mod_adul_2_loglik-Q_mod_adul_loglik,breaks=100)
 t.test(Q_mod_adul_2_loglik,Q_mod_adul_loglik)


#Q_mod_adol<-readRDS(file = "../../A_GeneratedFiles/modelfits/Q_3sw_gem_nogem_stan_adolescents.rds")
#Q_mod_adul<-readRDS(file = "../../A_GeneratedFiles/modelfits/Q_3sw_gem_nogem_stan_adults.rds")

```

# join posterior draws and join them with original dataframe.

```{r}
# make data in long format
adults<-Q_mod_adul%>%
  tidybayes::gather_draws(lr[participant],tau[participant,gem],sw[gem,participant,qual])%>%
  mutate(
    group="adults",
    player = keep_forfit_adults[participant]
  )# get back original participant index

adolescents<-Q_mod_adol%>%
  tidybayes::gather_draws(lr[participant],tau[participant,gem],sw[gem,participant,qual])%>%
  mutate(
    group="adolescents",
    player = keep_forfit_adolescents[participant]
  )

all_draws<-rbind(adults,adolescents)
#all_draws<-adults
# pivot wider first for joining with rest of the data.
all_draws_summarized<-all_draws%>%group_by(player,group,.variable,gem,qual)%>%
  dplyr::summarise(m_value=mean(.value))%>%pivot_wider(names_from = c(.variable,gem),values_from = m_value)

social_fits_d<-left_join(social_data,all_draws_summarized,by="player")

#saveRDS(all_draws,file = "A_GeneratedFiles/modelfits/draws_Q_gem_nogem.rds")
#saveRDS(social_fits_d,file = "A_GeneratedFiles/modelfits/summed_Q_gem_nogem.rds")
```

#

```{r}
adolescents%>%filter(.variable=="sw")%>%
  ggplot(aes(x=qual,y=.value,color=gem,group=gem))+
  stat_summary()


adults%>%filter(.variable=="sw")%>%
  ggplot(aes(x=qual,y=.value,color=gem,group=gem))+
  stat_summary()
```

# plot parameter estimates

```{r}

all_draws<-readRDS("./A_GeneratedFiles/modelfits/draws_Q_gem_nogem.rds")
library("tidybayes")
all_draws%>%group_by(participant,group,.variable,gem)%>%
  dplyr::summarise(m_value=mean(.value))%>%
  ggplot(aes(x=group,y=m_value,group=gem,color=as.factor(gem)))+
  #geom_point(position=position_dodge(0.9),alpha=0.1)+
  #geom_boxplot(position=position_dodge(0.1))+
  scale_color_discrete(name="gem found",labels=c("yes","no"))+
  stat_summary()+
  #scale_color_discrete()+
  facet_wrap(~ .variable,scales="free")+
  theme_bw(14)->plot

plot
```