---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2023-08-22'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4,nnet)
knitr::opts_knit$set(root.dir = here()) # set root fot the whole file
## loads the script where the learning models are specified (Q-learning, social Q-learning, UCB etc)
```

# About

This here loads all reasonable models and compares them and then plots some stuff for the winning model and makes simulations

```{r}
source('./C_modelfittingCode/learning_models.R')

## load functions that perform Maximul Likelihood Estimation
source("./C_modelfittingCode/models_mle.R")

## load functions that initialize the model fit
source("./C_modelfittingCode/model_fitting_functions_social_bandits.R")

## load behavioral data
social_data <-  read_csv(file = paste0("./data/social/data_social_all_participants.csv")) %>%#drop_na()
  filter(tot_points>0 & !is.na(demo_type))%>%#filter(player<30)%>%# get a sub-sample of both adults and adolescents 
  mutate(soctype=case_when(
    demo_type=="gem_found"~1,# i need that to index the different social weight parameters
    demo_type=="gem_not_found"~2,
    demo_type=="never_exploit"~3,
    demo_type=="no_gem"~4)
  )
```

# Load models
Down here i load all different model fits and check which model fits the data best.
Model comparsion is done based on predictive accuracy on a held out dataset.


```{r}
#path where model fits are stored
fits_path<-"A_GeneratedFiles/modelfits/social_models/all_envs/"

#define relevant models (those that have been fit on all environments and evaluated fit on a held out dataset)
modelspace_path<-c(
  "kalman_ucb_softmax_egreedy/",
  "kalman_ucb_sw_softmax_egreedy/",
  # "kalman_ucb_slr_softmax_egreedy/",
  #"kalman_ucb_asw_softmax_egreedy",
  "utility_2lr_4sw_softmax_egreedy/",
  "utility_2lr_sw_softmax_egreedy/",
  "utility_2lr_softmax_egreedy/"
  #"Q2lr_sw_2greedy/"#only greedy
)

#container for fit dfs
fit_dfs<-list()

for (i in 1:length(modelspace_path)){
  #list modelfits
  social_fits<-list.files(
    paste0(
      fits_path,
      modelspace_path[i]
    )
  )
  
  #only get dataframes
  social_fits_files<-social_fits[
    list.files(
      paste0(
        fits_path,
        modelspace_path[i]
      )
    )%>%startsWith(.,"data")
  ]
  
  #load fits
  fit_dfs[[i]]<-social_fits_files%>%
    purrr::map_dfr(.,~{
      #concat dfs
      d1<-readRDS(
        paste0(
          fits_path,
          modelspace_path[i],
          .x
        )
      )%>%tibble()%>%select(fit,player,group)%>%
        unique()%>%
        mutate(model=modelspace_path[i],
               model_idx=i
        )
      return(d1)
    })
}

fit_df<-do.call("rbind",fit_dfs)

```

# Compare models

```{r}
n_pars=c(4,5,8,5,4)

fit_df%>%group_by(model,group,player)%>%
  mutate(bic=n_pars[model_idx]*log(25*12)*2*fit)%>%
  group_by(model,group)%>%
  summarize(m_bic=mean(bic,na.rm=T))%>%
  group_by(group)%>%
  mutate(winner=ifelse(m_bic==min(m_bic),1,0))
```

```{r}
fit_df%>%group_by(model,group,player)%>%
  mutate(bic=n_pars[model_idx]*log(25*12)*2*fit)%>%
  group_by(model,group)%>%
  summarize(m_bic=mean(bic,na.rm=T))%>%
  group_by(group)%>%
  mutate(winner=ifelse(m_bic==min(m_bic),1,0))%>%
  mutate(m_bic=m_bic-min(m_bic))%>%
  ggplot(aes(x=model,y=m_bic,fill=group))+
  geom_bar(stat="identity",position="dodge")+
  ylab("bic_diff")+
  theme_minimal(14)+
  theme(axis.text.x = element_text(angle=45,hjust=1))
```

# Load winning model and plot parameters

```{r}
winnig_model_path<-"A_GeneratedFiles/modelfits/"
#   interesting that it only reads the correct df and not the list 
#only get dataframes
winning_fits_files<-list.files(winnig_model_path)[
  list.files(winnig_model_path)%>%startsWith(.,"data")
]

winning_model<-winning_fits_files%>%
  purrr::map_dfr(.,~{
    #concat dfs
    d1<-readRDS(
      paste0(
        winnig_model_path,
        .x
      )
    )
    return(d1)
  }
  )
```

# Load stan fits

```{r}
#all_draws<-readRDS("./A_GeneratedFiles/modelfits/draws_Q_gem_nogem.rds")

social_fits_d<-readRDS("A_GeneratedFiles/modelfits/summed_Q_gem_nogem.rds")

social_fits_d%>%ggplot(aes(x=group.y,y=tau_1))+
                         stat_summary()

```


# Simulate winning model.

```{r}

random_G2s <-  -2 * (log((1 / 64)) * 24)*12

source("./B_SimulationCode/load_environments_social_experiment.R") # environments
source("./C_modelfittingCode/models_mle.R")
source("./C_modelfittingCode/learning_models.R") # modelcode for simulation
source("./B_SimulationCode/sim_models.R") # modelcode for simulation

#environment files are in generated files
environments <- load_envs_social(path = "./A_GeneratedFiles/environments")
social_sims_plot_d <- list()
social_sims_plot_one <- list()

# ENVIRONMENTINDEXING FOR SIMS is 1:8
i <- 1
for (rpt in 1:1) {
  for (ppt in unique(social_fits_d$player)) {
    #print(ppt)
    # social data TODO: concatenate nonsocial data.
    d1 <- social_fits_d %>% filter(player == ppt) %>%
      mutate(z = points,
             choices = cells) %>% rowwise() %>%
      mutate(social_info = ifelse(social_info == 64, 1, social_info)) %>%
      ungroup()
    
    #### unpack parameters
    if(unique(d1$group.x)=="adults"){
      d1$tau_1=d1$tau_1*1.5
    }
    
    estimates <- c(
      unique(d1$lr_1),
      unique(d1$lr_2),
      unique(d1$tau_1),
      unique(d1$tau_2),
      unique(d1$sw_1),
      unique(d1$sw_2)
    )
    
    #collect fitted parameters and fit index and return
    cv <- exploreEnv_2lr_2sw_2tau(
      par = estimates,
      learning_model_fun = RW_Q,
      acquisition_fun = NULL,
      data = d1,
      envs = environments
    )
    cv$player = ppt
    cv$group = unique(d1$group.x)
    cv$run = rn
    social_sims_plot_one[[i]] <- cv
    # calculate mean
    i=i+1
  }
  #for additional repetitions
  social_sims_plot_d[[rpt]] <- do.call("rbind", social_sims_plot_one)
}
social_sims_plot_dhuge <- do.call("rbind", social_sims_plot_d)

```


#show performance
```{r fig.width=5}
gem<-environments%>%group_by(env)%>%
  summarise(gem=mean(gems))%>%arrange(env)%>%
  pull(gem)

social_sims_plot_dhuge %>%mutate(gem=ifelse(env_idx>4,1,0))%>%
  dplyr::group_by(trial, player, group,gem) %>%
  filter(trial > 0) %>%
  #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(z))%>%mutate(pats_or_sim="sims")->sims

social_fits_d %>%filter(!is.na(env_number))%>%mutate(gem=ifelse(env_number>4,1,0),group=group.x)%>%
  dplyr::group_by(trial, player,gem,group) %>%
  filter(trial > 0) %>% #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(points)) %>%mutate(pats_or_sim="pats")->pats

what_is_this<-left_join(social_sims_plot_dhuge,social_fits_d,by=c("player","trial","round"))

simsub_dat<-rbind(sims,pats)

labeller_patsim=c(
  "pats"="participants",
  "sims"="simulations"
)

labeller_gem=c(
  "0"="no gem",
  "1"="gem"
)

```

```{r}



simsub_dat%>%
  ggplot(aes(x = trial, y = m_rew, color = group,linetype=pats_or_sim)) +
  ggtitle("Simulations") +
  stat_summary() +
  stat_smooth(method = "lm") +
  facet_wrap(pats_or_sim~gem,
             labeller = labeller(
               pats_or_sim = labeller_patsim,
               gem=labeller_gem
             ))+
  theme_bw() -> comp_plot


comp_plot




what_is_this%>%ggplot(aes(x=trial,y =points, color = group.x)) +
  ggtitle("Participants") +
   stat_summary() +
  coord_cartesian(ylim=c(0,200))+
  scale_color_discrete(name="Agegroup")+
  facet_grid(soctype~gemlabel,labeller=labeller(soctype=soc_labs_2))+
  theme_bw()



what_is_this%>%ggplot(aes(x=trial,y =z.x, color = group.x)) +
  ggtitle("Simulations") +
  stat_summary() +
  coord_cartesian(ylim=c(0,200))+
  scale_color_discrete(name="Agegroup")+
  facet_grid(soctype~gemlabel,labeller=labeller(soctype=soc_labs_2))+
  theme_bw()
```

