---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2022-10-120'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(brms,tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4, ggthemes, cowplot,gghalves, runner)
options(buildtools.check = function(action) TRUE)
knitr::opts_knit$set(root.dir = here()) # set root fot the whole file

priors_bf <- c(
  prior_string("normal(0, 0.1)", class = "b")
)
```

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.



```{r}

random_G2s <-  -1 * (log((1 / 64)) * 24 * 4)

source(here("./B_SimulationCode","load_environments_social_experiment.R")) # environments
source(here("./B_SimulationCode","sim_models.R")) # modelcode for simulation

#environment files are in generated files
environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
social_sims_plot_d <- list()

environment_lookup<-environments%>%group_split(env)

social_data <-  read_csv(file = here("data","social","data_social_all_participants_08-2024.csv"))
# filter(p_value_rand<0.001)
#group_by(uniqueID)%>%
#filter(n()==300)%>%#only keep complete data
#mutate(round=rep(c(1:12),each=25))#new round index
social_data%>%
  ggplot(aes(x=p_value_rand,color=p_value_rand<0.05))+
  geom_histogram()


social_data%>%#filter(gem_found==1)%>%
  dplyr::group_by(uniqueID,round)%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=points,x=trial,color=as.factor(group)))+
  stat_summary()+
  #stat_smooth()+
  scale_color_brewer(palette="Accent")+
  facet_grid(qual~gem_found)


```

```{r }
social_data%>%#filter(gem_found==1)%>%
  dplyr::group_by(uniqueID,round)%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=points,x=trial,color=as.factor(group)))+
  #geom_point(size=0.1,shape=5)+
  stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(name="Age group",palette="Accent")+
  # facet_grid(qual~.)+
  theme_bw(21)



social_data%>%filter(gempresent==1)%>%
  select(uniqueID,round,group,gem_found)%>%
  dplyr::group_by(uniqueID,round,group)%>%
  unique()%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=gem_found,x=group,color=as.factor(group)))+
  #geom_point(size=0.1,shape=5)+
  stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(name="Age group",palette="Accent")+
  # facet_grid(qual~.)+
  theme_bw(21)


social_data%>%filter(gempresent==1)%>%
  select(uniqueID,round,group,gem_found,gem_found_how,round_gem_found)%>%
  dplyr::group_by(uniqueID,round,group,gem_found_how,round_gem_found)%>%
  unique()%>%filter(!is.na(gem_found_how))%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=round_gem_found,x=group,color=as.factor(group)))+
  #geom_point(size=0.1,shape=5)+
  stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(name="Age group",palette="Accent")+
  facet_grid(gem_found_how~.,scales="free")+
  theme_bw(21)
```




```{r}

## load behavioral data
#social_data <-  read_csv(file = here("data","social","data_social_all_participants.csv"))

# total max min for range normalization
max_gem<-social_data%>%filter(gempresent==1)%>%pull(points)%>%max()
max_no_gem<-social_data%>%filter(gempresent==0)%>%pull(points)%>%max()
min<-social_data%>%pull(points)%>%min()

social_data<-social_data%>%
  group_by(round,uniqueID,group)%>%
  mutate(often=abs(social_info-lag(social_info)))%>%
  mutate(change=ifelse(often==0,0,1))%>%
  mutate(streak=streak_run(change))%>%
  mutate(streak=ifelse(change==1,1,streak))%>%
  mutate(streak=ifelse(is.na(streak),1,streak))%>%
  mutate(streak=streak/25)%>%
  mutate(qual=case_when(
    demo_quality=="worst"~1,
    demo_quality=="medium"~2,
    demo_quality=="best"~3
  )
  )

social_data%>%#mutate(qual=ifelse(env_number==6,1,qual))%>%
  group_by(demo_quality)%>%
  group_by(z_points=(points-mean(points))/sd(points))%>%
  ggplot(aes(x=group,y=points,color=qual,group=interaction(qual,group)))+
  stat_summary()+
  facet_wrap(. ~ demo_quality,scales = "free")+
  theme_bw()


social_data%>%
  dplyr::group_by(round,uniqueID)%>%
  mutate(s_c=sum(copy))%>%
  ggplot(aes(y=s_c,x=group,color=as.factor(group)))+
  stat_summary()+
  scale_color_brewer(palette="Accent")+
  facet_wrap(gem_found~demo_quality)


social_data%>%
  dplyr::group_by(uniqueID,round)%>%
  mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=round_gem_found,x=group,color=as.factor(group)))+
  stat_summary()+
  scale_color_brewer(palette="Accent")+
  facet_wrap(gem_found_how~.,scales="free")


social_data%>%
  dplyr::group_by(uniqueID,round)%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=gem_found,x=trial,color=as.factor(group)))+
  stat_summary()+
  #stat_smooth()+
  scale_color_brewer(palette="Accent")+
  facet_wrap(demo_type~.)



social_data%>%
  #dplyr::group_by(uniqueID,round)%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=points,x=trial,color=as.factor(group)))+
  stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(palette="Accent")+
  theme_bw()

social_data%>%filter(trial!=25)%>%
  #dplyr::group_by(uniqueID,round)%>%
  #mutate(s_c=sum(gem_found))%>%
  ggplot(aes(y=copy,x=trial,shape=group))+
  stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(palette="Accent")+
  theme_bw()+
  facet_wrap(gem_found~.,labeller=label_both)+
  theme(aspect.ratio = 1)

social_data%>%select(gem_found_how,round,uniqueID,group)%>%
  unique()%>%group_by(group,gem_found_how)%>%filter(!is.na(gem_found_how))%>%
  summarise(count=n())%>%group_by(group)%>%
  mutate(count_p=count/sum(count))%>%
  ggplot(aes(y=count_p,x=gem_found_how,color=group))+
  geom_bar(stat="identity")+
  # stat_summary(position=position_dodge(0.9))+
  #stat_smooth()+
  scale_color_brewer(palette="Accent")+
  theme_bw()+
  facet_wrap(group~.)+
  theme(aspect.ratio = 1)

social_data%>%
  lmerTest::lmer(points~group*trial+(1 | uniqueID),data=.)%>%summary()

```


# Fit model to social data
This function fits the model specified in models_mle and stores the parameter estimates as well as the fit index (lower is better)
alongside the participant data in long format. In the future we want to modify this to fit different models

```{r}

fitagain=F
# 
cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)
#opts <- list(chunkSize=2)

## loads the script where the learning models are specified (Q-learning, social Q-learning, UCB etc)
source(here("./C_modelfittingCode/","diff_evo/","learning_models.R"))

## load functions that perform Maximul Likelihood Estimation
source(here("./C_modelfittingCode/","diff_evo/","models_mle_2.R"))

## load functions that initialize the model fit
source(here("./C_modelfittingCode/","diff_evo/","model_fitting_functions_social_bandits_2.R"))

# load environments into workspace
source(here("./B_SimulationCode","load_environments_social_experiment.R")) # environments

#Iteration: 200 bestvalit: 435.902250 bestmemit:    8.708619    0.021584    0.005103    0.336568
if (fitagain){
  social_fits <- foreach(
    player_nr = unique(social_data$uniqueID),
    .packages = c("DEoptim", "tidyverse","here","data.table"),
    .combine = "rbind"
  ) %dopar%{
    environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
    
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    d1 <- social_data %>% 
      filter(uniqueID == player_nr) %>%
      mutate(z =points,
             choices = choice
      )%>%ungroup()
    
    cv <- tryCatch(        # might throw an error, just continue if it does and dont be annoying
      {
        fit_policy(d1=d1)
      },
      warning = function(w) {
        # Handle warnings
        message("Warning occurred: ", conditionMessage(w))
        fit_policy(d1=d1)
      },
      error = function(e) {
        # Handle errors
        message("Error occurred: ", conditionMessage(e))
        return(NA)  # Return a default value
      }
    )
    
    print(cv)
    # collect fit indices
    
    d1$fit <- unlist(cv[1])# is always the fit index
    d1$p1<-unlist(cv[2])
    d1$p2<-unlist(cv[3])#low
    d1$p3<-unlist(cv[4])#medium
    d1$p4<-unlist(cv[5])#high
    
    return(d1)
    
  }
  
  saveRDS(social_fits,file = here("A_GeneratedFiles","modelfits","tau_slearn_v_shape2.rds"))
}else{
  social_fits<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_v_shape2.rds"))%>%ungroup()
  # social_fits<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_no_prior.rds"))%>%ungroup()
  # social_fits_prior<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_prior.rds"))%>%ungroup()
  # social_fits_old<-readRDS(file = here("A_GeneratedFiles","modelfits","2tau_slearn_rangs.rds"))%>%ungroup()
  
}


plot_df<-social_fits %>%#filter(sw_1>0)%>%
  dplyr::select(uniqueID, group,"p1","p2","p3","p4")%>%unique()%>%
  pivot_longer(c("p1","p2","p3","p4"))%>%
  # filter(value>0.001 & value <900)%>%
  mutate(var_greek=case_when(
    name=="p1"~"alpha",
    name=="p2"~"tau",
    name=="p3"~"omega",
    name=="p4"~"zeta"
  )
  )

facet_labels<-labeller(name=c(
  "p1" = "Learning rate",
  "p2" = "Temperature",
  "p3" = "Social learning rate",
  "p4" = "Prior copy probability"
)
)

parameters<-plot_df%>%mutate(value=ifelse(name=="p4",1/(1+exp(2.5/value)),value))%>%
  ggplot(aes(x=group,y=value,color=group))+
  theme_bw(14)+
  stat_boxplot()+
  geom_point(size=0.3,shape=5)+
  scale_color_brewer(name="",palette = "Set2")+
  scale_x_discrete(name="Agegroup")+
  scale_y_continuous(name="Parameter value")+
  facet_wrap(. ~ name,scales="free_y",labeller = facet_labels,nrow = 2)+
  theme(aspect.ratio = 1)

ggsave(parameters,filename=here::here("plots","parameter_plot.png"))
```

# group differences in parameter

```{r}

mod_lr<-plot_df%>%filter(var_greek=="alpha")%>%brms::brm(value~group,prior = priors_bf,sample_prior = T,data=.)
mod_temp<-plot_df%>%filter(var_greek=="tau")%>%brms::brm(value~group,prior = priors_bf,sample_prior = T,data=.)
mod_soclr<-plot_df%>%filter(var_greek=="omega")%>%brms::brm(value~group,prior = priors_bf,sample_prior = T,data=.)
mod_priocp<-plot_df%>%filter(var_greek=="zeta")%>%brms::brm(value~group,prior = priors_bf,sample_prior = T,data=.)


post_lr<-bayestestR::describe_posterior(mod_lr)
post_temp<-bayestestR::describe_posterior(mod_temp)
post_soclr<-bayestestR::describe_posterior(mod_soclr)
post_cp<-bayestestR::describe_posterior(mod_priocp)

bf_lr<-bayestestR::bayesfactor_parameters(mod_lr)
bf_temp<-bayestestR::bayesfactor_parameters(mod_temp)
bf_soclr<-bayestestR::bayesfactor_parameters(mod_soclr)
bf_cp<-bayestestR::bayesfactor_parameters(mod_priocp)

```

#"Posterior" sims
Simulating choices from the policy model
```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)

for (rptx in 1:20){
  social_sims_plot_d[[rptx]]<-foreach(
    player_nr = unique(social_fits$uniqueID),
    .packages = c("DEoptim", "dplyr","here"),
    .combine = "rbind"
  ) %dopar%{
    print(player_nr)
    # social data TODO: concatenate nonsocial data.
    dat <- social_fits %>% filter(
      uniqueID == player_nr,
    ) 
    
    estimates <- c(
      unique(dat$p1),
      unique(dat$p2),
      unique(dat$p3),
      unique(dat$p4)
    )
    
    rounds<-unique(dat$round)
    ####
    sim_dat<-NULL
    for (r in rounds) { # loop through rounds in roundList
      d1<-dat%>%filter(round==r)
      env_nr<-unique(d1$env_number)
      # simulations for parameter recovery
      sim_dat_r <- s_policy_shaping_sim(
        par = estimates,
        si = d1$social_info,
        envs = environment_lookup[[env_nr]]
      ) # only try one sub
      sim_dat_r$round=r
      sim_dat_r$player = player_nr
      sim_dat_r$group = unique(d1$group)
      sim_dat_r$run<-rptx
      sim_dat<-rbind(sim_dat,sim_dat_r)
    }
    # cv$run = rptx
    return(sim_dat)
  }
}
#
#concat simulation runs
social_sims<- do.call("rbind", social_sims_plot_d)

social_sims$pars_sim[1][[1]]
```

# parameter recovery

```{r}
fitagain=T
#Iteration: 200 bestvalit: 435.902250 bestmemit:    8.708619    0.021584    0.005103    0.336568
if (fitagain){
  social_recovery <- foreach(
    player_nr = unique(social_sims$player),
    .packages = c("DEoptim", "tidyverse","here","data.table"),
    .combine = "rbind"
  ) %dopar%{
    environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
    
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    d1 <- social_sims %>% 
      filter(player == player_nr, run==1) %>%
      mutate(z =z,
             choices = index
      )%>%ungroup()
    
    cv <- tryCatch(        # might throw an error, just continue if it does and dont be annoying
      {
        fit_policy(d1=d1)
      },
      warning = function(w) {
        # Handle warnings
        message("Warning occurred: ", conditionMessage(w))
        fit_policy(d1=d1)
      },
      error = function(e) {
        # Handle errors
        message("Error occurred: ", conditionMessage(e))
        return(NA)  # Return a default value
      }
    )
    
    print(cv)
    # collect fit indices
    
    d1$fit <- unlist(cv[1])# is always the fit index
    d1$p1<-unlist(cv[2])
    d1$p2<-unlist(cv[3])#low
    d1$p3<-unlist(cv[4])#medium
    d1$p4<-unlist(cv[5])#high
    
    return(d1)
    
  }
  
  saveRDS(social_recovery,file = here("A_GeneratedFiles","modelfits","policy_recovery.rds"))
}else{
  social_recovery<-readRDS(file = here("A_GeneratedFiles","modelfits","policy_recovery.rds"))%>%ungroup()
  # social_fits<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_no_prior.rds"))%>%ungroup()
  # social_fits_prior<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_prior.rds"))%>%ungroup()
  # social_fits_old<-readRDS(file = here("A_GeneratedFiles","modelfits","2tau_slearn_rangs.rds"))%>%ungroup()
}
```

```{r}
recov_df<-social_recovery%>%mutate(
  which="recovery",
  ppt=ifelse(group=="adults",player+1000,player)# unique player idx
)%>%select(p1,p2,p3,p4,ppt,group,which)%>%unique()

fits_df<-social_fits%>%mutate(
  which="original",
  ppt=ifelse(group=="adults",player+1000,player)
)%>%select(p1,p2,p3,p4,ppt,group,which)%>%unique()

recovery_df_plots<-rbind(recov_df,fits_df)%>%
  pivot_wider(id_cols = ppt,names_from = c(which),values_from = c(p1,p2,p3,p4))

recovery_df_plots%>%ggplot(aes(x=p1_original,p1_recovery))+
  geom_point()+
  geom_smooth()

recovery_df_plots%>%ggplot(aes(x=p2_original,p2_recovery))+
  geom_point() +
  geom_smooth()

recovery_df_plots%>%ggplot(aes(x=p3_original,p3_recovery))+
  geom_point() +
  geom_smooth()

recovery_df_plots%>%ggplot(aes(x=p4_original,p4_recovery))+
  geom_point() +
  geom_smooth()

fits_df
recov_df
```


```{r}
#summarize
social_sims %>% 
  mutate(uniqueID=player)%>%
  dplyr::group_by(trial, player, group) %>%
  filter(trial > 0) %>%
  dplyr::summarise(m_rew = mean(z))%>%mutate(pats_or_sim="sims")->sims

social_fits %>%filter(!is.na(env_number))%>%mutate(gem=ifelse(env_number>4,1,0),group=group)%>%
  dplyr::group_by(trial, uniqueID,group,age) %>%
  filter(trial > 0) %>% #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(points)) %>%mutate(pats_or_sim="pats")->pats
simsub_dat<-rbind(sims,pats)

# make plot comparing learning trajectories of participants with model
simsub_dat%>%#filter(age>30 | age <17)%>%
  ggplot(aes(x = trial, y = m_rew,color=group, linetype = pats_or_sim,shape=pats_or_sim)) +
  stat_summary() +
  scale_shape_discrete(name= "",labels=c("simulations","participants"))+
  scale_linetype_manual(name= "Age-group",labels=c("simulations","participants"),values=c("solid","dashed"))+
  scale_y_continuous(name="Average reward")+
  scale_x_continuous(name="Trial")+
  scale_color_brewer(name="Agegroup",palette = "Set2")+
  guides(fill=F,shape=F,linetype=F,color=F)+
  facet_wrap(.~pats_or_sim,nrow=2,labeller = labeller(pats_or_sim=c("pats"="Participants","sims"="Model simulations")))+
  theme_bw()+
  theme(aspect.ratio = 1)-> comp_plot

```

```{r fig.height=7}

cowplot::plot_grid(comp_plot,parameters+theme(aspect.ratio = 1),nrow=2)
```




# make plot demonstrating social influece
the interesting parts:
1) exploit gem when before there was quite some exploring
2) exploit non-gem when there is a gem

```{r}
sis<-list(
  social_samples=c(12,12,5,7,2,2,2,2,14,14,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11),# exploring first, then gem
  social_samples_2=c(2,2,2,3,3,3,3,3,63,4,14,17,16,16,9,2,2,2,17,2,43,4,3,43,40)# reasonable at first, then bad
)
envs_social<-environment_lookup[[5]]

#parameters to simulate
parvec_adol<-c(0.5,0.1,0.3,1.5)
parvec_adul<-c(0.5,0.3,0.1,1.5)


#simulate over three types of social information
adol_sim<-NULL
adul_sim<-NULL

for (rep in 1:100){# 100 repetitions
  for (si in c(1:2)){# two types of social info (one time good, another time bad)
    adol_sim_1<-s_policy_shaping_sim(
      par = parvec_adol,
      envs = envs_social,
      si=sis[[si]]
    ) %>%mutate(si=si)
    
    adul_sim_1<-s_policy_shaping_sim(
      par = parvec_adul,#[.x,],
      envs = envs_social,
      si=sis[[si]]
    )%>%mutate(si=si)
    # concatanete simulations
    adul_sim<- rbind(adul_sim_1,adul_sim)
    adol_sim<- rbind(adol_sim_1,adol_sim)
  }
}

sims<-rbind(
  adul_sim%>%mutate(group="adul"),
  adol_sim%>%mutate(group="adol")
)

```

```{r}
sims%>%filter(si==1)%>%
  ggplot(aes(x=trial,y=p_copy,color=group))+
  geom_vline(xintercept = 12)+
  stat_smooth()+
  scale_color_brewer(name="Agegroup",palette = "Set2")+
  scale_y_continuous(name="Probability to copy demonstrator")+
  coord_cartesian(ylim=c(0,0.2))+
  guides(color=F)+
  theme_bw(14)+
  theme(aspect.ratio = 1)

sims%>%filter(si==2)%>%
  ggplot(aes(x=trial,y=p_copy,color=group))+
  geom_vline(xintercept = 4)+
  stat_smooth()+
  scale_color_brewer(name="Agegroup",palette = "Set2")+
  scale_y_continuous(name="Probability to copy demonstrator")+
  coord_cartesian(ylim=c(0,0.2))+
  guides(color=F)+
  theme_bw(14)+
  theme(aspect.ratio = 1)

sims%>%filter(si==1)%>%
  ggplot(aes(x=trial,y=z,color=group))+
  geom_vline(xintercept = 12)+
  stat_smooth()+
  scale_color_brewer(name="Agegroup",palette = "Set2")+
  scale_y_continuous(name="Average reward")+
   guides(color=F)+
  coord_cartesian(ylim=c(0,200))+
  theme_bw(14)

sims%>%filter(si==2)%>%
  ggplot(aes(x=trial,y=z,color=group))+
  geom_vline(xintercept = 4)+
  stat_smooth()+
  scale_color_brewer(name="Agegroup",palette = "Set2")+
  scale_y_continuous(name="Average reward")+
  coord_cartesian(ylim=c(0,200))+
  guides(color=F)+
  theme_bw()
```

```{r fig.width=10,fig.height=5}

modelling_figure<-plot_grid(parameter_plot,comp_plot,labels=c("","d"),rel_widths = c(0.9,1))

ggsave("sims_learn_tau.png",plot = modelling_figure,width = 11,height = 5)
```

# recovery

This here is simulating data based on model fits
```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)

social_data_recov_s_w<-list()
for (i in 1:100){
  
  social_data_recov_s_w[[i]]<-foreach(
    player_nr = unique(social_fits$uniqueID),
    .packages = c("DEoptim", "dplyr","here"),
    .combine = "rbind"
  ) %dopar%{
    
    # get data from one player
    dat <- social_fits %>% filter(
      uniqueID == player_nr,
    )
    
    #### unpack parameters from model fits
    estimates<- c(
      unique(dat$p1),
      unique(dat$p2),
      unique(dat$p3),
      unique(dat$p4)
    )
    
    sim_dat<-NULL
    for (r in unique(dat$round)) { # loop through rounds in roundList
      d1<-dat%>%filter(round==r)
      env_nr<-unique(d1$env_number)
      # simulations for parameter recovery
      sim_dat_r <- s_policy_shaping_sim(
        par = estimates,
        si = d1$social_info,
        envs = environment_lookup[[env_nr]]
      ) # only try one sub
      sim_dat_r$round=r
      sim_dat_r$player = player_nr
      sim_dat_r$group = unique(d1$group)
      sim_dat_r$env<-env_nr
      sim_dat<-rbind(sim_dat,sim_dat_r)
    }
    
    return(sim_dat)
  }
}

saveRDS(social_data_recov_s_w,file = here("A_GeneratedFiles","recovery_sims.rds"))


srt```


#

```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)
#container for the parameter recovery analysis
social_recovery<-list()
for (i in 1:25){
  social_data_recov<-social_data_recov_s_w[[i]]
  social_recovery[[i]] <- foreach(
    player_nr = unique(social_data_recov$player),
    .packages = c("DEoptim", "tidyverse","here","data.table"),
    .combine = "rbind"
  ) %dopar%{
    environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
    
    #for(player_nr in unique(social_data$player)){
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    # social data TODO: concatenate nonsocial data.
    #print(s)
    print(player_nr)
    d1 <- social_data_recov %>% filter(
      player == player_nr
      #soc_info_round == s
    ) %>%
      #filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = z, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = index,
             env_number=env_idx
      ) %>%ungroup()
    #rounds <- unique(d1$round)
    #only fit if you have 25 klicks.
    
    d_recov <- fit_policy(d1 = d1,environments=environments) # only try one sub
    
    # collect fit indices
    
    d_recov$fit <- unlist(cv[1])
    #d1$lr_p <- unlist(cv[2])
    #d1$intercept <- unlist(cv[2])
    d_recov$lr<-unlist(cv[2])
    d_recov$tau_1<-unlist(cv[3])
    d_recov$sw_1<-unlist(cv[4])
    d_recov$prior<-unlist(cv[5])
    # d1$lr<-unlist(cv[4])
    #d1$ut<-unlist(cv[4])
    # d1$streak_w<-unlist(cv[4])
    # d1$prior<-unlist(cv[6])
    # d1$sw <- unlist(cv[4])
    return(d_recov)
  }
}
saveRDS(social_recovery,file = here("A_GeneratedFiles","recovery_sw3.rds"))

```

```{r}
sw_recov<-tibble()
estimates<-foreach(
  player_nr = unique(social_fits$uniqueID),
  .packages = c("DEoptim", "dplyr","here"),
  .combine = "rbind"
) %do%{
  
  # print(rptx)
  Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
  print(player_nr)
  
  # social data TODO: concatenate nonsocial data.
  d1 <- social_fits %>% filter(
    uniqueID == player_nr,
  ) %>%
    #filter(gempresent == 0) %>%  # for now only have rounds without gems 
    group_by(round) %>%
    mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
           social_info = social_info,
           choices = cells,
           soc_info_round=demo_quality,
    ) %>%ungroup()
  #### unpack parameters
  lr<-unique(d1$lr)
  tau<-unique(d1$tau_1)
  sw<-unique(d1$sw_1)
  prior<-unique(d1$prior) 
  return(tibble(lr=lr,tau=tau,sw=sw,prior=prior))
}

recovery=tibble()
for (i in 1:20){
  ah<-tibble(
    fit_sw=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par3)%>%unlist(),
    fit_lr=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par1)%>%unlist(),
    fit_tau=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par2)%>%unlist(),
    sim_sw=estimates$sw,
    sim_tau=estimates$tau,
    sim_lr=estimates$lr,
    idx=i
  )
  recovery<- rbind(recovery,ah)
}

recovery_real<-recovery%>%group_by(sim_sw,sim_tau,sim_lr)%>%
  summarise(
    rec_sw=mean(fit_sw),
    rec_lr=mean(fit_lr),
    rec_tau=mean(fit_tau)
  )

cor(recovery_real$rec_sw,recovery_real$sim_sw,method = "spearman")

```



```{r}

rec_sw_sim_sw<-recovery_real%>%
  ggplot(aes(x=rec_sw,y=sim_sw))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *omega))+  
  theme_bw()

rec_lr_sim_sw<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_sw))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *alpha))+    
  theme_bw()

rec_tau_sim_sw<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_sw))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *tau))+  
  theme_bw()





rec_sw_sim_lr<-recovery_real%>%ggplot(aes(x=rec_sw,y=sim_lr))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *omega))+  
  theme_bw()

rec_lr_sim_lr<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_lr))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *alpha))+  
  theme_bw()

rec_tau_sim_lr<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_lr))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *tau))+  
  theme_bw()


rec_sw_sim_tau<-recovery_real%>%ggplot(aes(x=rec_sw,y=sim_tau))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("fitted " *omega))+
  theme_bw()


rec_lr_sim_tau<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_tau))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("fitted " *alpha))+
  theme_bw()


rec_tau_sim_tau<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_tau))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("simulated " *tau))+
  theme_bw()

recovery_plot<-plot_grid(
  plot_grid(rec_sw_sim_sw,rec_lr_sim_sw,rec_tau_sim_sw,ncol = 1),
  plot_grid(rec_sw_sim_lr,rec_lr_sim_lr,rec_tau_sim_lr,ncol=1),
  plot_grid(rec_sw_sim_tau,rec_lr_sim_tau,rec_tau_sim_tau,ncol=1),
  ncol=3)
```








#complete modelling figure
```{r fig.width=12}

parameter_plot<-plot_grid(alpha,omega,tau,labels="auto",nrow=3)

modelling_figure_1<-plot_grid(
  comp_plot,
  plot_grid(
    NULL,
    recovery_plot,
    NULL,ncol=3,
    rel_widths = c(0.02,1,0.22)
  )
  ,labels=c("d","e"),
  nrow=2
)

modelling_figure<-plot_grid(parameter_plot,modelling_figure_1,ncol=2,rel_widths = c(0.3,1))

modelling_figure
```






```{r}


dummy<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
  # filter(demo_quality=="worst")%>%
  #filter(player==2)%>%
  ggplot(aes(x=trial,y=copy_util,color=as.factor(env_idx)))+
  geom_point(aes(group=player),alpha=0.3)+
  scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
  scale_y_continuous(name="Utility of copying [au]")+
  stat_smooth(size=2)+
  facet_grid(env_idx ~. ,scales="free")+
  guides(fill=F)+
  theme_bw(15)



Utility<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
  # filter(demo_quality=="worst")%>%
  #filter(player==2)%>%
  ggplot(aes(x=trial,y=copy_util,color=as.factor(env_idx)))+
  #geom_point(aes(group=player),alpha=0.3)+
  scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
  scale_y_continuous(name="Utility of copying [au]")+
  stat_smooth(size=2,method = "loess",fill=NA)+
  facet_grid(env_idx ~. ,scales="free")+
  guides(fill=F,color=F)+
  theme_bw(15)+  
  theme(
    #aspect.ratio = 1,
    strip.background = element_blank(),
    strip.text.y = element_blank()
  )


Value<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
  # filter(demo_quality=="worst")%>%
  #filter(player==2)%>%
  ggplot(aes(x=trial,y=copy_prob,color=as.factor(env_idx)))+
  scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
  scale_y_continuous(name=expression("Copy probability: "* (1+exp(-Q_copy))^ -1))+
  #stat_summary(size=1,geom="line")+
  stat_smooth(size=2,method = "loess",fill=NA)+
  coord_cartesian(ylim=c(0,0.2))+
  facet_grid(env_idx ~. )+
  guides(fill=F,color=F)+
  theme_bw(15)+
  theme(
    #aspect.ratio = 1,
    strip.background = element_blank(),
    strip.text.y = element_blank()
  )

legend<-get_legend(dummy)
model_demo_plot<-plot_grid(Utility,NULL,Value,legend,ncol=4,rel_widths = c(1,0.1,1,0.3))

ggsave(model_demo_plot,filename=here::here("plots","model_dynamics.png"),width = 10,height=4.5)
```




```{r}
samples_gem_late<-c(1,1,5,7,2,2,2,2,14,14,16,16,2,2,17,17,17,11,11,11,11,11,11,11,11)
samples_gem_early<-c(1,1,5,7,2,2,2,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11)

```


