---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2022-10-120'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4,nnet)
knitr::opts_knit$set(root.dir = here()) # set root fot the whole file
refit=T
```

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.

```{r}

## load behavioral data
social_data <-  read_csv(file = paste0("./data/social/data_social_all_participants.csv")) #%>% 
#filter(uniqueID < 30)#%>%
#filter(tot_points>0)# get a sub-sample of both adults and adolescents 

```

# Fit model to social data
This function fits the model specified in models_mle and stores the parameter estimates as well as the fit index (lower is better)
alongside the participant data in long format. In the future we want to modify this to fit different models

```{r}
#
modelpath="./C_modelfittingCode/diff_evo/"

refit=T
if (refit){
  cl <- makeCluster(detectCores(), type = 'PSOCK')
  registerDoParallel(cl)
  
  ## loads the script where the learning models are specified (Q-learning, social Q-learning, UCB etc)
  source('./C_modelfittingCode/diff_evo/learning_models.R')
  
  ## load functions that perform Maximul Likelihood Estimation
  source("./C_modelfittingCode/diff_evo/models_mle.R")
  
  ## load functions that initialize the model fit
  source("./C_modelfittingCode/diff_evo/model_fitting_functions_social_bandits.R")
  
  social_fits <- foreach(
    player_nr = unique(social_data$uniqueID),
    .packages = c("DEoptim", "dplyr","nnet"),
    .combine = "rbind"
  ) %dopar% {
    #for(player_nr in unique(social_data$player)){
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    print(player_nr)
    
    # social data TODO: concatenate nonsocial data.
    d1 <- social_data %>% filter(uniqueID == player_nr) %>%
      # filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = cells
      ) %>% rowwise() %>%
      mutate(social_info = ifelse(social_info == 64, 1, social_info)) %>%
      ungroup()
    
    rounds <- unique(d1$round)
    cv<-NA
    ####
    #### crossvalidation
    #### leaves out one round and fits model on the other rounds. 
    #### then evaluates the modelfit on the held out data
    for (r in rounds) { # loop through rounds in roundList
      cv_one<-fit_2lr_sw_2gre(d1 = d1,leaveoutindex = r)
      cv <-rbind(cv,cv_one) # only try one sub
    }
    # collect fit indices and compute mean
    d1$fit <- mean(cv[,2],na.rm=T)
    d1$lr_p <- mean(cv[,3],na.rm=T)
    d1$lr_n <- mean(cv[,4],na.rm=T)
    d1$epsilon_gem <- mean(cv[,5],na.rm=T)
    d1$epsilon_no_gem <- mean(cv[,6],na.rm=T)
    
    #d1$prior<-unlist(cv[5])
    saveRDS(cv, file = paste0("../A_GeneratedFiles/modelfits/social_models/all_envs/Q2lr_sw_2greedy/fit", player_nr, ".rds"))
        saveRDS(d1, file = paste0("../A_GeneratedFiles/modelfits/social_models/all_envs/Q2lr_sw_2greedy/data_fit", player_nr, ".rds"))
    return(d1)
  }
} else{#read from disk if refit is false
  fits_path<-"A_GeneratedFiles/modelfits/social_models/all_envs/Q2lr_sw_2greedy/"
  
  social_fits<-list.files(fits_path)%>%
    purrr::map_dfr(.,~{
      dat<-readRDS(paste0(fits_path,.))
      #get back player number from fit.
      d1 <- social_data %>% filter(uniqueID == parse_number(.x))
      #glue all data
      d1$fit <- unlist(dat[1])
      d1$lr_p <- unlist(dat[2])
      d1$lr_n <- unlist(dat[3])
      d1$epsilon_gem <- unlist(dat[4])
      d1$epsilon_no_gem <- unlist(dat[5])
    })
}
```

# Evaluate fit 


```{r}

social_fits %>%
  dplyr::select(uniqueID, group, fit) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = fit, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary() +
  theme_minimal()


# check learning rates
social_fits %>%
  select(player, group, lr_p) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = lr_p, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary() +
  theme_minimal()

social_fits %>%
  select(player, group, lr_n) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = lr_n, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary() +
  theme_minimal()

# check greedy difference in kids and adults 
social_fits %>%
  dplyr::select(player, group, epsilon_gem) %>%
  distinct() %>%
  #mutate(asymmetry_index = (lr_p-lr_n)/(lr_p + lr_n)) %>%
  ggplot(aes(y = epsilon_gem, x=group, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary()+
  theme_minimal()


# check greedy difference in kids and adults 
social_fits %>%
  dplyr::select(player, group, epsilon_no_gem) %>%
  distinct() %>%
  #mutate(asymmetry_index = (lr_p-lr_n)/(lr_p + lr_n)) %>%
  ggplot(aes(y = epsilon_no_gem, x=group, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary()+
  theme_minimal()

```


simulate!

```{r}

random_G2s <-  -1 * (log((1 / 64)) * 24 * 4)

source("./B_SimulationCode/load_environments_social_experiment.R") # environments
source("./B_SimulationCode/sim_models.R") # modelcode for simulation

#environment files are in generated files
environments <- load_envs_social(path = "./A_GeneratedFiles/")
social_sims_plot_d <- list()
social_sims_plot_one <- list()

# ENVIRONMENTINDEXING FOR SIMS is 1:8
#for (i in 1:100){
#  print(i)
# social_sims_plot_d[[i]]<-foreach(
#   player_nr = unique(social_fits$player),
i <- 1
rn <- i
#   .packages = c("DEoptim", "dplyr"),
#   .combine="rbind"
# ) %do% {
social_fits_dNa<-social_fits

#filter out participants that could not be fit and wierd trials that have na values in environments
social_fits_dNa<-social_fits_dNa%>%filter(!is.na(fit),!is.na(env_number))

for (player_nr in unique(social_fits_dNa$uniqueID)) {
  Xnew <-
    as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
  output <- c()
  print(player_nr)
  
  # social data TODO: concatenate nonsocial data.
  d1 <- social_fits_dNa %>% filter(uniqueID == player_nr) %>%
    group_by(round) %>%
    mutate(z = points,
           #(points - mean(points)) /sd(points),
           social_info = social_info,
           choices = cells) %>% rowwise() %>%
    mutate(social_info = ifelse(social_info == 64, 1, social_info)) %>%
    ungroup()
  
  #### unpack parameters
  estimates <- c(unique(d1$lr_p),
                 unique(d1$lr_n),
                 unique(d1$epsilon_gem),
                 unique(d1$epsilon_no_gem)
  )
  ####
  #for (r in rounds) { # loop through rounds in roundList
  cv <- simumalte_2lr_sw_2greedy(
    par = estimates,
    learning_model_fun = RW_Q_2,
    acquisition_fun = ucb,
    data = d1,
    envs = environments
  ) # only try one sub
  #collect fitted parameters and fit index and return
  #social_data$modelfit=cv
  #output <- rbind(output, cv)
  #}
  cv$player = player_nr
  cv$group = unique(d1$group)
  cv$run = rn
  social_sims_plot_one[[player_nr]] <- cv
}

social_sims_plot_d[[i]] <- do.call("rbind", social_sims_plot_one)

#}

social_sims_plot_dhuge <- do.call("rbind", social_sims_plot_d)
```

```{r fig.width=5}
gem<-environments%>%group_by(env)%>%
  summarise(gem=mean(gems))%>%arrange(env)%>%
  pull(gem)

social_sims_plot_dhuge %>%mutate(gem=ifelse(envi>4,1,0))%>%
  dplyr::group_by(trial, player, group,gem) %>%
  filter(trial > 0) %>%
  #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(z)) %>%
  ggplot(aes(x = trial, y = m_rew, color = group)) +
  ggtitle("Simulations") +
  stat_summary() +
  stat_smooth(method = "lm") +
  facet_wrap(~gem)+
  theme_bw() -> sims

social_fits %>%filter(!is.na(env_number))%>%mutate(gem=ifelse(env_number>4,1,0))%>%
  dplyr::group_by(trial, player, group,gem) %>%
  filter(trial > 0) %>% #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(points)) %>%
  ggplot(aes(x = trial, y = m_rew, color = group)) +
  ggtitle("Participants") +
  stat_summary() +
  stat_smooth(method = "lm") +
  facet_wrap(~gem)+
  theme_bw() -> ppts

cowplot::plot_grid(sims, ppts)


```

