---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2022-10-120'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(brms,tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4, ggthemes, cowplot,gghalves, runner)

knitr::opts_knit$set(root.dir = here()) # set root fot the whole file
```

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.



```{r}

random_G2s <-  -1 * (log((1 / 64)) * 24 * 4)

source(here("./B_SimulationCode","load_environments_social_experiment.R")) # environments
source(here("./B_SimulationCode","sim_models.R")) # modelcode for simulation

#environment files are in generated files
environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
social_sims_plot_d <- list()

environment_lookup<-environments%>%group_split(env)

social_data <-  read_csv(file = here("data","social","data_social_all_participants_08-2024.csv"))%>%
  group_by(uniqueID)%>%
  filter(n()==300)%>%#only keep complete data
  mutate(round=rep(c(1:12),each=25))#new round index

```




```{r}

## load behavioral data
#social_data <-  read_csv(file = here("data","social","data_social_all_participants.csv"))

# total max min for range normalization
max_gem<-social_data%>%filter(gempresent==1)%>%pull(points)%>%max()
max_no_gem<-social_data%>%filter(gempresent==0)%>%pull(points)%>%max()
min<-social_data%>%pull(points)%>%min()

social_data<-social_data%>%
  group_by(round,uniqueID,group)%>%
  mutate(often=abs(social_info-lag(social_info)))%>%
  mutate(change=ifelse(often==0,0,1))%>%
  mutate(streak=streak_run(change))%>%
  mutate(streak=ifelse(change==1,1,streak))%>%
  mutate(streak=ifelse(is.na(streak),1,streak))%>%
  #  mutate(copy=ifelse(social_info==cells,1,0))%>%
  # mutate(copy_old=ifelse(social_info_use=="copy",1,0))%>%
  #  ungroup()%>%
  mutate(streak=streak/25)%>%
  mutate(qual=case_when(
    demo_quality=="worst"~1,
    demo_quality=="medium"~2,
    demo_quality=="best"~3
  )
  )

social_data%>%#mutate(qual=ifelse(env_number==6,1,qual))%>%
  group_by(qual)%>%
  group_by(z_points=(points-mean(points))/sd(points))%>%
  #filter(qual!=3)%>%#filter(env_number==6)%>%
  ggplot(aes(x=group,y=points,color=qual,group=interaction(qual,group)))+
  stat_summary()+
  # stat_summary(aes(group=interaction(qual,group)),geom="line")
  facet_wrap(. ~ qual,scales = "free")+
  theme_bw()


social_data%>%ggplot(aes(y=copy,x=group,color=as.factor(group)))+
  stat_summary()+
  scale_color_brewer(palette="Accent")+
  facet_wrap(.~demo_type)

```


# Fit model to social data
This function fits the model specified in models_mle and stores the parameter estimates as well as the fit index (lower is better)
alongside the participant data in long format. In the future we want to modify this to fit different models

```{r}

fitagain=T
# 
#cl <- makeCluster(detectCores()-8, type = 'PSOCK')
#registerDoParallel(cl)
#opts <- list(chunkSize=2)

## loads the script where the learning models are specified (Q-learning, social Q-learning, UCB etc)
source(here("./C_modelfittingCode/","diff_evo/","learning_models.R"))

## load functions that perform Maximul Likelihood Estimation
source(here("./C_modelfittingCode/","diff_evo/","models_mle_2.R"))

## load functions that initialize the model fit
source(here("./C_modelfittingCode/","diff_evo/","model_fitting_functions_social_bandits_2.R"))

# load environments into workspace
source(here("./B_SimulationCode","load_environments_social_experiment.R")) # environments

#Iteration: 200 bestvalit: 435.902250 bestmemit:    8.708619    0.021584    0.005103    0.336568
if (fitagain){
  social_fits <- foreach(
    player_nr = unique(social_data$uniqueID),
    .packages = c("DEoptim", "tidyverse","here","data.table"),
    .combine = "rbind"
  ) %dopar%{
    environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
    
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    print(player_nr)
    d1 <- social_data %>% filter(
      uniqueID == player_nr
      #soc_info_round == s
    ) %>%
      #filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = choice
      ) %>%ungroup()

        cv <- tryCatch(
      {
        # might throw an error
        fit_slr(d1 = d1,environments=environments) # only try one sub
      },
      warning = function(w) {
        # Handle warnings
        message("Warning occurred: ", conditionMessage(w))
        fit_slr(d1 = d1,environments=environments) # only try one sub
      #  return(NA)  # Return a default value
      },
      error = function(e) {
        # Handle errors
        message("Error occurred: ", conditionMessage(e))
        return(NA)  # Return a default value
      }
    )
    
    print(cv)
    # collect fit indices
    
    d1$fit <- unlist(cv[1])

    d1$lr<-unlist(cv[2])
    d1$tau_1<-unlist(cv[3])
    d1$sw_1<-unlist(cv[4])
   # d1$prior<-unlist(cv[5])

    return(d1)
    
  }
  
  saveRDS(social_fits,file = here("A_GeneratedFiles","modelfits","tau_slearn_v_shape.rds"))
}else{
  #social_fits<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_prior.rds"))%>%ungroup()
  # social_fits<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_no_prior.rds"))%>%ungroup()
  #social_fits_prior<-readRDS(file = here("A_GeneratedFiles","modelfits","tau_slearn_rangs_prior.rds"))%>%ungroup()
  #social_fits_old<-readRDS(file = here("A_GeneratedFiles","modelfits","2tau_slearn_rangs.rds"))%>%ungroup()
  
}
```

# Evaluate fit 


```{r}
social_data%>%
  group_by(round,player,group)%>%
  mutate(often=abs(social_info-lag(social_info)))%>%
  mutate(change=ifelse(often==0,0,1))%>%
  mutate(streak=streak_run(change))%>%
  mutate(streak=ifelse(change==1,1,streak))%>%
  mutate(copy=ifelse(social_info_use=="copy",1,0))%>%
  ggplot(aes(x=streak,y=copy,color=group))+
  stat_summary()+
  facet_wrap(.~demo_type)


social_data%>%
  group_by(round,player,group)%>%
  mutate(often=abs(social_info-lag(social_info)))%>%
  mutate(change=ifelse(often==0,0,1))%>%
  mutate(streak=streak_run(change))%>%
  mutate(streak=ifelse(change==1,1,streak))%>%
  mutate(copy=ifelse(social_info_use=="copy",1,0))%>%
  ggplot(aes(x=demo_quality,y=copy,color=group))+
  stat_summary()#+
# facet_wrap(.~demo_quality)

social_fits %>%
  dplyr::select(uniqueID, group, fit) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = fit, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary() +
  theme_minimal()


argh<-social_data%>%filter(demo_quality=="best",env_number==6)%>%
  select(cell,social_info,z,copy,soc_info_round,demo_quality,env_number)

social_data
social_data%>%filter(copy==1)%>%
  select(cell,cells,social_info,points,copy,soc_info_round,env_number,social_info_p1)->ah

ah%>%filter(cell+1 != cells)
ah%>%filter(cell == social_info)
ah%>%filter(cells == social_info_p1)

ah%>%filter(cells == social_info_p1,soc_info_round==1912)#%>%pull(env_number)%>%unique()

environments%>%filter(env==6)%>%pull(Mean)->ah
ah[20]
ah[20]
```

```{r}

social_fits %>%
  dplyr::select(uniqueID, group, fit) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = fit, color = group)) +
  #geom_line(aes(group=index))+
  stat_summary() +
  theme_minimal()
```

#Parameter plots.

```{r}

plot_df<-social_fits %>% #filter(soc_info_round!=795)%>%
  dplyr::select(uniqueID, group,"lr","tau_1","sw_1","prior")%>%unique()%>%
  pivot_longer(c("lr","tau_1","sw_1","prior"))%>%
  # filter(value>0.001 & value <900)%>%
  mutate(var_greek=case_when(
    name=="sw_1"~"alpha",
    name=="tau_1"~"tau",
    name=="lr"~"omega",
    name=="prior"~"zeta"))


plot_df%>%filter(var_greek=="alpha")%>%
  ggplot(aes(x=group,y=value,group=group))+
  #scale_y_log10(name="MLE (logscale)")+
  #geom_half_boxplot(notch = TRUE) +
  geom_half_point(alpha = .4) +
  scale_x_discrete(name="")+
  stat_summary(
    geom = "pointrange",
    #size = 2,
    #stroke = 0.5,
    color = "black",
    fill = "orange",
    position = position_dodge(width = .75),
    shape=23
  ) +
  #scale_color_discrete()+
  facet_wrap( ~ var_greek,scales="free",labeller = label_parsed)+
  theme_bw(14)->alpha



plot_df%>%filter(var_greek=="omega")%>%
  ggplot(aes(x=group,y=value,group=group))+
  scale_y_continuous(name="MLE")+
  #geom_half_boxplot(notch = TRUE) +
  geom_half_point(alpha = .4) +
  scale_x_discrete(name="")+
  stat_summary(
    geom = "pointrange",
    #size = 2,
    #stroke = 0.5,
    color = "black",
    fill = "orange",
    position = position_dodge(width = .75),
    shape=23
  ) +
  #scale_color_discrete()+
  facet_wrap( ~ var_greek,scales="free",labeller = label_parsed)+
  theme_bw(14)->omega


plot_df%>%filter(var_greek=="tau")%>%
  ggplot(aes(x=group,y=value,group=group))+
  scale_y_log10(name="MLE (logscale)")+
  #geom_half_boxplot(notch = TRUE) +
  geom_half_point(alpha = .4) +
  scale_x_discrete(name="")+
  stat_summary(
    geom = "pointrange",
    #size = 2,
    #stroke = 0.5,
    color = "black",
    fill = "orange",
    position = position_dodge(width = .75),
    shape=23
  ) +
  #scale_color_discrete()+
  facet_wrap( ~ var_greek,scales="free",labeller = label_parsed)+
  theme_bw(14)->tau

```


```{r}
plot_df%>%filter(var_greek=="zeta")%>%
 # ggplot(aes(x=group,y=1/(1+exp(-value/0.01)),group=group))+
  ggplot(aes(x=group,y=value,group=group))+
  scale_y_continuous(name="MLE")+
  #geom_half_boxplot(notch = TRUE) +
  #geom_jitter()+
  scale_x_discrete(name="")+
  stat_summary()+
  #scale_color_discrete()+
  facet_wrap( ~ var_greek,scales="free",labeller = label_parsed)+
  theme_bw(14)->zeta

parameter_plot<-cowplot::plot_grid(alpha,omega,tau,zeta,labels="auto")

```

# parameter inference

```{r}

prior3 <- prior_string("cauchy(0, 2.5)", class = "b")

alpha_mod<-social_fits %>% #filter(soc_info_round!=795)%>%
  dplyr::select(uniqueID, group, sw_1)%>%unique()%>%
  mutate(sw_1=(((sw_1-mean(sw_1))/sd(sw_1))))%>%
  brms::brm(sw_1~  group,prior=prior3,
            sample_prior=T,
            data=.,
            cores=6,
            iter=20000,
            #family=exponential(link = "log"),
            file = here("A_GeneratedFiles","alpha_brm.rds"),file_refit = "always")
hypothesis(alpha_mod,"groupadults<0",alpha=0.05)

omega_mod<-social_fits %>% #filter(soc_info_round!=795)%>%
  dplyr::select(uniqueID, group, lr)%>%unique()%>%
  mutate(lr=(((lr-mean(lr))/sd(lr))))%>%
  brms::brm(lr~  group,prior=prior3,
            sample_prior=T,
            data=.,
            cores=6,
            iter=20000,
            file = here("A_GeneratedFiles","omega_brm.rds"))
hypothesis(omega_mod,"groupadults=0",alpha=0.05)


tau_mod<-social_fits %>% #filter(soc_info_round!=795)%>%
  dplyr::select(uniqueID, group, tau_1)%>%unique()%>%
  mutate(tau_1=(((tau_1-mean(tau_1))/sd(tau_1))))%>%
  brms::brm(tau_1~  group,prior=prior3,
            sample_prior=T,
            data=.,
            cores=6,
            iter=20000,
            file = here("A_GeneratedFiles","tau_1_brm.rds"))
hypothesis(tau_mod,"groupadults>0",alpha=0.05)


tau_mod<-social_fits %>% #filter(soc_info_round!=795)%>%
  dplyr::select(uniqueID, group, tau_1,soc_info_round,demo_quality)%>%unique()%>%
  lm(tau_1~  group, prior=prior3,sample_prior=T,data=.,cores=4)
```

"Posterior" sims

```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)

for (rptx in 1:20){
  print(rptx)
  social_sims_plot_d[[rptx]]<-foreach(
    player_nr = unique(social_fits$uniqueID),
    .packages = c("DEoptim", "dplyr","here"),
    .combine = "rbind"
  ) %do%{
    
    # print(rptx)
    Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    print(player_nr)
    
    # social data TODO: concatenate nonsocial data.
    d1 <- social_fits %>% filter(
      uniqueID == player_nr,
    ) %>%
      #filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = cells
      ) %>%ungroup()
    
    #### unpack parameters
    lr<-unique(d1$lr)
    tau<-unique(d1$tau_1)
    sw<-unique(d1$sw_1)
    prior<-unique(d1$prior)
    
    estimates <- c(
      lr,
      tau,
      sw,
      prior
    )
    ####
    #for (r in rounds) { # loop through rounds in roundList
    cv <- s_learn_prior_sim(
      par = estimates,
      learning_model_fun = RW_Q,
      data = d1,
      envs = environments
    ) # only try one sub
    
    cv$player = player_nr
    cv$group = unique(d1$group)
    cv$run = rptx
    return(cv)
    #  social_sims_plot_one[[i]] <- cv
    # i = i+1  
  }
}
#
#social_sims_plot_d[[rpt]] <- do.call("rbind", social_sims_plot_one)
social_sims<- do.call("rbind", social_sims_plot_d)
#}
```


```{r}


social_sims<-social_sims %>%mutate(gem=ifelse(env_idx>4,1,0))%>%
  mutate(uniqueID=player)

social_sims %>% 
  mutate(uniqueID=player)%>%
  dplyr::group_by(trial, player, group,gem) %>%
  filter(trial > 0) %>%
  #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(z))%>%mutate(pats_or_sim="sims")->sims

social_fits %>%filter(!is.na(env_number))%>%mutate(gem=ifelse(env_number>4,1,0),group=group)%>%
  dplyr::group_by(trial, uniqueID,gem,group,age) %>%
  filter(trial > 0) %>% #filter(group!="adults")%>%
  dplyr::summarise(m_rew = mean(points)) %>%mutate(pats_or_sim="pats")->pats
simsub_dat<-rbind(sims,pats)

simsub_dat%>%#filter(age>30 | age <17)%>%
  ggplot(aes(x = trial, y = m_rew, linetype = group,shape=group)) +
  #ggtitle("Trial wise reward") +
  stat_summary() +
  scale_shape_discrete(name= "Age-group",labels=c("adolescents","adults"))+
  scale_linetype_discrete(name= "Age-group",labels=c("adolescents","adults"))+
  scale_y_continuous(name="average reward")+
  scale_x_continuous(name="klick")+
  stat_smooth(method = "lm") +
  facet_wrap(pats_or_sim~.,labeller = labeller(pats_or_sim=c("pats"="participants","sims"="model simulations")))+
  theme_bw() -> comp_plot

```

```{r fig.width=10,fig.height=5}

modelling_figure<-plot_grid(parameter_plot,comp_plot,labels=c("","d"),rel_widths = c(0.9,1))

ggsave("sims_learn_tau.png",plot = modelling_figure,width = 11,height = 5)
```

```{r}

#what_is_this<-left_join(social_sims,social_fits,by=c("uniqueID","trial","round","group"))
advisor_qual<-social_fits%>%select(demo_quality,round,uniqueID,soc_info_round)

social_sims<-social_sims%>%
  mutate(soc_info_round=demo_quality)%>%select(-demo_quality)


w_qual<-right_join(social_sims,advisor_qual,by=c("soc_info_round","uniqueID","round"))
#cowplot::plot_grid(sims, ppts)


w_qual_plot<-w_qual%>%group_by(group,trial,uniqueID,run,demo_quality,gem)%>%
  summarise(copy_prob=mean(copy_prob),
            rew=mean(z))

w_qual_plot%>%
  ggplot(aes(x=trial,y=copy_prob,color=group))+
  stat_summary(aes(group=interaction(group,run)),geom="point",alpha=0.1)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(name="copy probability")+
  scale_x_continuous(name="klick")+
  stat_smooth()+
  #geom_point()+
  facet_wrap(.~demo_quality)+
  theme_bw()


w_qual_plot%>%
  ggplot(aes(x=trial,y=rew,color=group))+
  stat_summary(aes(group=interaction(group,run)),geom="point",alpha=0.1)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(name="copy probability")+
  scale_x_continuous(name="klick")+
  stat_smooth()+
  #geom_point()+
  facet_wrap(gem~demo_quality)+
  theme_bw()


w_qual_plot%>%
  ggplot(aes(x=trial,y=rew,color=group))+
  stat_summary(aes(group=interaction(group,run)),geom="point",alpha=0.1)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(name="copy probability")+
  scale_x_continuous(name="klick")+
  stat_smooth()+
  #geom_point()+
  #facet_wrap(gem~demo_quality)+
  theme_bw()

simsub_dat

```

# recovery
Here i fit the model again on the simulated data from above. 

```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)

#sw<-seq(0,0.3,length.out=20)
#i=0
social_data_recov_s_w<-list()
for (i in 1:25){
  # print(rptx)
  #i=i+1
  social_data_recov_s_w[[i]]<-foreach(
    player_nr = unique(social_fits$uniqueID),
    .packages = c("DEoptim", "dplyr","here"),
    .combine = "rbind"
  ) %dopar%{
    
    # print(rptx)
    Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    print(player_nr)
    
    # social data TODO: concatenate nonsocial data.
    d1 <- social_fits %>% filter(
      uniqueID == player_nr,
    ) %>%
      #filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = cells,
             soc_info_round=demo_quality,
      ) %>%ungroup()
    
    #### unpack parameters
    lr<-unique(d1$lr)
    tau<-unique(d1$tau_1)
    sw<-unique(d1$sw_1)
    prior<-unique(d1$prior)
    
    estimates <- c(
      lr,
      tau,
      sw,
      prior
    )
    ####
    #for (r in rounds) { # loop through rounds in roundList
    cv <- s_learn_prior_sim(
      par = estimates,
      learning_model_fun = RW_Q,
      data = d1,
      envs = environments
    ) # only try one sub
    
    cv$player = player_nr
    cv$group = unique(d1$group)
    cv$run = rptx
    return(cv)
    #  social_sims_plot_one[[i]] <- cv
    # i = i+1  
  }
}

#stopCluster()
```


#

```{r}

cl <- makeCluster(detectCores()-8, type = 'PSOCK')
registerDoParallel(cl)
#container for the parameter recovery analysis
social_recovery<-list()
for (i in 1:100){
  social_data_recov<-social_data_recov_s_w[[i]]
  social_recovery[[i]] <- foreach(
    player_nr = unique(social_data_recov$player),
    .packages = c("DEoptim", "tidyverse","here","data.table"),
    .combine = "rbind"
  ) %dopar%{
    environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
    
    #for(player_nr in unique(social_data$player)){
    Xnew <- as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    # social data TODO: concatenate nonsocial data.
    #print(s)
    print(player_nr)
    d1 <- social_data_recov %>% filter(
      player == player_nr
      #soc_info_round == s
    ) %>%
      #filter(gempresent == 0) %>%  # for now only have rounds without gems 
      group_by(round) %>%
      mutate(z = z, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
             social_info = social_info,
             choices = index,
             env_number=env_idx
      ) %>%ungroup()
    #rounds <- unique(d1$round)
    #only fit if you have 25 klicks.
    
    d_recov <- fit_slr(d1 = d1,environments=environments) # only try one sub
    
    # collect fit indices
    
    d_recov$fit <- unlist(cv[1])
    #d1$lr_p <- unlist(cv[2])
    #d1$intercept <- unlist(cv[2])
    d_recov$lr<-unlist(cv[2])
    d_recov$tau_1<-unlist(cv[3])
    d_recov$sw_1<-unlist(cv[4])
    d_recov$prior<-unlist(cv[5])
    # d1$lr<-unlist(cv[4])
    #d1$ut<-unlist(cv[4])
    # d1$streak_w<-unlist(cv[4])
    # d1$prior<-unlist(cv[6])
    # d1$sw <- unlist(cv[4])
    return(d_recov)
  }
}
saveRDS(social_recovery,file = here("A_GeneratedFiles","recovery_sw3.rds"))

```

```{r}
sw_recov<-tibble()
estimates<-foreach(
  player_nr = unique(social_fits$uniqueID),
  .packages = c("DEoptim", "dplyr","here"),
  .combine = "rbind"
) %do%{
  
  # print(rptx)
  Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
  print(player_nr)
  
  # social data TODO: concatenate nonsocial data.
  d1 <- social_fits %>% filter(
    uniqueID == player_nr,
  ) %>%
    #filter(gempresent == 0) %>%  # for now only have rounds without gems 
    group_by(round) %>%
    mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
           social_info = social_info,
           choices = cells,
           soc_info_round=demo_quality,
    ) %>%ungroup()
  #### unpack parameters
  lr<-unique(d1$lr)
  tau<-unique(d1$tau_1)
  sw<-unique(d1$sw_1)
  prior<-unique(d1$prior) 
  return(tibble(lr=lr,tau=tau,sw=sw,prior=prior))
}

recovery=tibble()
for (i in 1:20){
  ah<-tibble(
    fit_sw=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par3)%>%unlist(),
    fit_lr=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par1)%>%unlist(),
    fit_tau=social_recovery[[i]]%>%
      as_tibble()%>%
      pull(par2)%>%unlist(),
    sim_sw=estimates$sw,
    sim_tau=estimates$tau,
    sim_lr=estimates$lr,
    idx=i
  )
  recovery<- rbind(recovery,ah)
}

recovery_real<-recovery%>%group_by(sim_sw,sim_tau,sim_lr)%>%
  summarise(rec_sw=mean(fit_sw),
            rec_lr=mean(fit_lr),
            rec_tau=mean(fit_tau)
  )

cor(recovery_real$rec_sw,recovery_real$sim_sw,method = "spearman")

```

```{r}

rec_sw_sim_sw<-recovery_real%>%
  ggplot(aes(x=rec_sw,y=sim_sw))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *omega))+  
  theme_bw()

rec_lr_sim_sw<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_sw))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *alpha))+    
  theme_bw()

rec_tau_sim_sw<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_sw))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *omega))+
  scale_x_continuous(name=expression("fitted " *tau))+  
  theme_bw()





rec_sw_sim_lr<-recovery_real%>%ggplot(aes(x=rec_sw,y=sim_lr))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *omega))+  
  theme_bw()

rec_lr_sim_lr<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_lr))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *alpha))+  
  theme_bw()

rec_tau_sim_lr<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_lr))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *alpha))+
  scale_x_continuous(name=expression("fitted " *tau))+  
  theme_bw()






rec_sw_sim_tau<-recovery_real%>%ggplot(aes(x=rec_sw,y=sim_tau))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("fitted " *omega))+
  theme_bw()


rec_lr_sim_tau<-recovery_real%>%ggplot(aes(x=rec_lr,y=sim_tau))+
  geom_point(alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="grey",fill="grey")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("fitted " *alpha))+
  theme_bw()


rec_tau_sim_tau<-recovery_real%>%ggplot(aes(x=rec_tau,y=sim_tau))+
  geom_point(color="red",alpha=0.1)+
  ggpubr::stat_cor(method = "pearson")+
  stat_smooth(method="lm",color="red",fill="red")+
  scale_y_continuous(name=expression("simulated " *tau))+
  scale_x_continuous(name=expression("simulated " *tau))+
  theme_bw()

recovery_plot<-plot_grid(
  plot_grid(rec_sw_sim_sw,rec_lr_sim_sw,rec_tau_sim_sw,ncol = 1),
  plot_grid(rec_sw_sim_lr,rec_lr_sim_lr,rec_tau_sim_lr,ncol=1),
  plot_grid(rec_sw_sim_tau,rec_lr_sim_tau,rec_tau_sim_tau,ncol=1),
  ncol=3)
```

#complete modelling figure
```{r fig.width=12}

parameter_plot<-plot_grid(alpha,omega,tau,labels="auto",nrow=3)

modelling_figure_1<-plot_grid(
  comp_plot,
  plot_grid(
    NULL,
    recovery_plot,
    NULL,ncol=3,
    rel_widths = c(0.02,1,0.22)
  )
  ,labels=c("d","e"),
  nrow=2
)

modelling_figure<-plot_grid(parameter_plot,modelling_figure_1,ncol=2,rel_widths = c(0.3,1))

modelling_figure
```


```
library(corrplot)
M = cor(recovery_real,method = "spearman")
corrplot(M, method = 'number') # colorful number

PerformanceAnalytics::chart.Correlation(recovery_real[c(1,4,2,6,3,5)], pch="+",method="spearman")
```

```{r}
grr<-social_recovery[[1]]%>%
  as_tibble()%>%
  pull(par4)
# get values inside of range
w_qual%>%mutate(copy=ifelse(index==social_info,1,0))%>%filter(trial>10)%>%
  group_by(round,demo_quality,uniqueID,group)%>%
  summarize(
    m_ut=mean(copy_util),
    m_copy=mean(copy,na.rm=T)
  )%>%filter(m_ut>-3 & m_ut<250)->u_for_plot

w_qual%>%filter(trial>2)%>%mutate(copy=ifelse(index==social_info,1,0))%>%
  group_by(round,demo_quality,uniqueID,group)%>%summarize(m=mean(copy,na.rm=T))->q_for_plot

u_for_plot%>%ggplot(aes(x=group,y=m_ut,color=group))+
  stat_summary()+
  facet_wrap(.~demo_quality)

u_for_plot%>%ggplot(aes(x=group,y=m_copy,color=group))+
  stat_summary()+
  facet_wrap(.~demo_quality)

social_fits%>%filter(trial>2)%>%mutate(copy=ifelse(cells==social_info,1,0))%>%
  group_by(round,demo_quality,uniqueID,group)%>%summarize(m=mean(copy,na.rm=T))%>%
  ggplot(aes(x=group,y=m,color=group))+
  stat_summary()+
  facet_wrap(.~demo_quality)
```


```{r fig.width=6 fig.height=2.5}
w_qual_plot%>%#filter(trial>10)%>%
  ggplot(aes(x=group,y=copy_prob,color=group))+
  stat_summary()+
  # stat_summary(aes(group=uniqueID), alpha = .4,geom="point") +
  scale_x_discrete(name="")+
  #stat_boxplot()+
  #scale_y_log10()
  stat_summary(
    geom = "point",
    size = 1,
    stroke = 0.5,
    color = "black",
    fill = "orange",
    position = position_dodge(width = .75),
    shape=23
  ) +
  #geom_point()+
  facet_wrap(.~demo_quality)+
  theme_bw()

#scale_y_log10(name="MLE")+

```




# Social rewards simulate!

```{r}

random_G2s <-  -1 * (log((1 / 64)) * 24 * 4)

source(here("./B_SimulationCode","load_environments_social_experiment.R")) # environments
source(here("./B_SimulationCode","sim_models.R")) # modelcode for simulation

#environment files are in generated files
environments <- load_envs_social(path = here("A_GeneratedFiles","environments/"))
social_sims_plot_d <- list()
social_sims_plot_one <- list()

#cl <- makeCluster(detectCores()-8, type = 'PSOCK')
#registerDoParallel(cl)

i=1
social_fits_w<-social_fits#%>%filter(group=="adolescents")

for (rpt in 1){
  social_sims_plot_d[[rpt]] <- foreach(
    player_nr = unique(social_fits_w$uniqueID),
    .packages = c("DEoptim", "dplyr"),
    .combine = "rbind"
  ) %do% {
    #for (player_nr in unique(social_fits_w$uniqueID)){
    
    Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
    print(player_nr)
    
    # social data TODO: concatenate nonsocial data.
    d1 <- social_fits_w %>% dplyr::filter(uniqueID == player_nr) %>%
      group_by(round) %>%
      mutate(z = points,
             #(points - mean(points)) /sd(points),
             social_info = social_info,
             choices = cells) 
    
    ####
    # print("do")
    cv <- social_rewards(
      data = d1,
      envs = environments
    ) # only try one sub
    
    cv$player = player_nr
    cv$group = unique(d1$group)
    cv$run = rpt
    return(cv)
    #  social_sims_plot_one[[i]] <- cv
    # i = i+1  
  }
  #social_sims_plot_d[[rpt]] <- do.call("rbind", social_sims_plot_one)
}
#}

social_sims_plot_dhuge <- do.call("rbind", social_sims_plot_d)

social_sims_plot_dhuge%>%
  ggplot(aes(x=social_reward,fill=demo_type))+
  geom_histogram()


# social_sims_plot_dhuge%>%mutate(uniqueID=player)%>%
#   select(uniqueID,group,round,social_reward,trial)%>%
#   left_join(.,social_data,by=c("uniqueID","round","trial"))%>%
#   ggplot(aes(x=social_reward,fill=demo_type))+
#   geom_histogram()+
#   facet_wrap(.~ group.x)

```


```{r}
social_fits%>%
  ggplot(aes(x=uniqueID))+
  geom_histogram(binwidth=1)


social_fits%>%group_by(uniqueID,round,group)%>%
  mutate(any_copy=ifelse(any(social_info_use=="copy"),1,0))%>%
  count(social_info_use)%>%filter(social_info_use=="copy")%>%
  ggplot(aes(x=group,y=n,color=group))+
  stat_summary(position="dodge")

social_fits%>%
  summarise()

```




















# make plot demonstrating SI
```{r}

social_data_recov_s_w<-foreach(
  player_nr = unique(social_fits$uniqueID),
  .packages = c("DEoptim", "dplyr","here"),
  .combine = "rbind"
) %do%{
  
  # print(rptx)
  Xnew <-as.matrix(expand.grid(0:7, 0:7)) # do this outside the loop for better speed
  print(player_nr)
  
  # social data TODO: concatenate nonsocial data.
  d1 <- social_fits %>% filter(
    uniqueID == player_nr,
  ) %>%
    #filter(gempresent == 0) %>%  # for now only have rounds without gems 
    group_by(round) %>%
    mutate(z = points, #(points - mean(points)) / sd(points), ventually figure out what is the best outcome for this
           social_info = social_info,
           choices = cells,
           soc_info_round=demo_quality,
    ) %>%ungroup()
  
  #### unpack parameters
  lr<-unique(d1$lr)
  tau<-unique(d1$tau_1)
  sw<-0.0001
  prior<--0.2
  
  estimates <- c(
    lr,
    tau,
    sw,
    prior
  )
  ####
  #for (r in rounds) { # loop through rounds in roundList
  cv <- s_learn_prior_sim(
    par = estimates,
    learning_model_fun = RW_Q,
    data = d1,
    envs = environments
  ) # only try one sub
  
  cv$player = player_nr
  cv$group = unique(d1$group)
  cv$run = rptx
  return(cv)
  #  social_sims_plot_one[[i]] <- cv
  # i = i+1  
}
```


```{r}

social_data_recov_s_w%>%filter(env %in% c(6))%>%
  # filter(demo_quality=="worst")%>%
  #filter(player==2)%>%
  ggplot(aes(x=trial,y=copy_prob))+
  #  geom_point()+
  stat_summary()+
  facet_grid(. ~ env)



social_data_recov_s_w%>%
  filter(env %in% c(6))%>%
  select(index,social_info)


environments$env%>%unique()

envs<-environments%>%filter(env==6)%>%pull(Mean)

envs[60]
```


```{r}


dummy<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
# filter(demo_quality=="worst")%>%
#filter(player==2)%>%
ggplot(aes(x=trial,y=copy_util,color=as.factor(env_idx)))+
geom_point(aes(group=player),alpha=0.3)+
scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
scale_y_continuous(name="Utility of copying [au]")+
stat_smooth(size=2)+
facet_grid(env_idx ~. ,scales="free")+
guides(fill=F)+
theme_bw(15)



Utility<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
# filter(demo_quality=="worst")%>%
#filter(player==2)%>%
ggplot(aes(x=trial,y=copy_util,color=as.factor(env_idx)))+
#geom_point(aes(group=player),alpha=0.3)+
scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
scale_y_continuous(name="Utility of copying [au]")+
stat_smooth(size=2,method = "loess",fill=NA)+
facet_grid(env_idx ~. ,scales="free")+
guides(fill=F,color=F)+
theme_bw(15)+  
theme(
#aspect.ratio = 1,
strip.background = element_blank(),
strip.text.y = element_blank()
)


Value<-social_data_recov_s_w%>%filter(env_idx %in% c(5,6))%>%
# filter(demo_quality=="worst")%>%
#filter(player==2)%>%
ggplot(aes(x=trial,y=copy_prob,color=as.factor(env_idx)))+
scale_color_manual(name="Quality of\n Social Info",labels=c("Good","Bad"),values=c("red","chartreuse3"))+
scale_y_continuous(name=expression("Copy probability: "* (1+exp(-Q_copy))^ -1))+
#stat_summary(size=1,geom="line")+
stat_smooth(size=2,method = "loess",fill=NA)+
coord_cartesian(ylim=c(0,0.2))+
facet_grid(env_idx ~. )+
guides(fill=F,color=F)+
theme_bw(15)+
theme(
#aspect.ratio = 1,
strip.background = element_blank(),
strip.text.y = element_blank()
)

legend<-get_legend(dummy)
model_demo_plot<-plot_grid(Utility,NULL,Value,legend,ncol=4,rel_widths = c(1,0.1,1,0.3))

ggsave(model_demo_plot,filename=here::here("plots","model_dynamics.png"),width = 10,height=4.5)
```
