---
title: "Analyses_Pilot"
author: "Simon"
date: '2022-06-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(here,tidyverse,brms)
```

## Social Bandits Explore

Here we will have a first look at the pilot data

```{r load}
pilot_data<-read_csv(file = "./Behav_Data/Pilot1/clean_data_1.csv")
env_gem="environments_gem_250_var25max.json"
env_no_gem="environments_no_gem_var25max.json"

```

## Test

Switches given gem
average exploration given gemenot notgemenv


```{r pressure, echo=FALSE}
pilot_data%>%group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  pivot_longer(cols=c(exploit,explore),names_to = "explore_exploit")%>%
  ggplot(aes(x=points,y=value,color=explore_exploit))+
  stat_summary()+
  theme_minimal(20)
```
```{r}
pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  mutate(gem=ifelse(points>150,1,0))%>%
  brm(data=.,explore~gem+(1|player),cores=4,family = bernoulli)

``` 

```{r}
pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  mutate(out_cat=case_when(points>150~1,
                           points<0~3,
                           TRUE~2
  )
  )%>%pivot_longer(cols=c(exploit,explore),names_to = "explore_exploit")%>%
  ggplot(aes(x=out_cat,y=value,color=explore_exploit,shape=explore_exploit))+
  stat_summary(size=1)+
  stat_summary(geom="line")+
  scale_y_continuous(name="Proportion")+
  scale_x_continuous(name="Category",breaks=c(1,2,3),labels=c("gem","no gem","loss"))+
  theme_minimal(20)





pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  mutate(out_cat=case_when(points>150~1,
                           points<0~3,
                           TRUE~2
    )
  )%>%
  brm(data=.,explore~as.factor(out_cat)+(1|player),cores=4,family = bernoulli)
```

# average trial number with gem found
Could figure out how to do this on the fly
```{r eval=FALSE}
#max(pilot_data$player)

pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  group_by(player,round)%>%
  mutate(trial=1:n())%>%
  filter(gem==1) 
  
  
  
  mutate(out_cat=case_when(points>150~1,
                           points<0~3,
                           TRUE~2
    )
  )

```

# exploration environments
Average exploration in different environments
Exploration is greater in nongem envs.
```{r}
pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  ggplot(aes(x=as.factor(gempresent),y=explore))+
  stat_summary()+
  scale_x_discrete(name="gem present",breaks=c(0,1),labels=c("No","Yes"))+
  scale_y_continuous(name="proportion exploration")+
  theme_minimal(20)


```

# reward environments
When there is no gem present, people encounter more losses

```{r}
pilot_data%>%
  group_by(player)%>%
  mutate(exploit=ifelse(lead(cells)==cells,1,0),
         explore=ifelse(lead(cells)!=cells,1,0))%>%
  mutate(out_cat=case_when(points>0~"reward",
                           points<=0~"loss",
                           #TRUE>2
    )
  )%>%
  ggplot(aes(x=out_cat,fill=as.factor(gempresent)))+
  geom_bar(stat="count",position="dodge")+
  scale_fill_discrete(name="Gem Present")+
  theme_minimal(20)

  #facet_wrap(~gempresent)
```
