---
title: "Explore_data_for_social information"
author: "Andrea"
date: "2022-11-03"
output: html_document
---


```{r}
pacman::p_load(tidyverse, rjson, data.table, gghalves, plotly, gganimate, av, colorspace, here)
`%!in%` = Negate(`%in%`)
```


# Identify participants that can provide different types of social information

## relevant variables

- n of switches
- n of consecutive clicks
- n of gems founds

n of point searned vs. expected points (better than chance)

```{r load data, echo=FALSE, warning=FALSE, message=FALSE }

explore_data <- read_csv(file = paste0(here(), "/data/data_coord.csv"))
 
explore_data <- explore_data %>% 
  filter(player != 188) %>% 
  group_by(player, round) %>% 
    mutate(trial = 1:25,
           unique_rounds = cur_group_id())
  
  
#nogems <- subset(explore_data, gempresent == 0)



```


# finding social info:

criteria:
- points are representative to average
- gem not found before round 10
- exploration is conistent



## find average points when a gem is found
```{r}

points_when_gem_found <- explore_data %>% 
  group_by(player, gempresent, tot_points, env_number) %>% 
  filter(gempresent == 1 & sum(gem) > 1) %>% 
  select(player, gempresent, tot_points, unique_rounds, env_number) %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(env_number) %>% 
  mutate(performance_group = ntile(tot_points, 3))


# distribution of point when gem is found

points_when_gem_found %>% 
  ggplot() +
  geom_histogram(aes( x = tot_points, fill = factor(performance_group)), binwidth = 40)+
 #, color = "white") +
  #geom_vline(aes(xintercept = mean(tot_points)), lty = 2, size = 1, color = 'black') + 
  #geom_half_point(aes(x = factor(gempresent), y = points), alpha = 0.02) +
  #theme_bw(base_size = 20) +
  facet_wrap(~gempresent+gem_found)
  guides(fill = "none")



```

## timing

now filter for gem not found before round 10

```{r}
# list of players 

avg_rounds <- points_when_gem_found %>% 
  filter(performance_group == 2 | performance_group == 1) %>% 
  ungroup() %>% 
  select(unique_rounds)

avg_rounds <- avg_rounds$unique_rounds

early_gems_idx <- which(explore_data$gem & explore_data$trial <= 10)
round_to_exclude <- unique(explore_data$unique_rounds[early_gems_idx])


late_gems <- explore_data %>% 
  filter(unique_rounds %in% avg_rounds)%>% 
  filter(unique_rounds %!in% round_to_exclude)

how_may_late_gems <- late_gems%>% 
  group_by(env_number) %>% 
  summarise(sum = n())

```

# visualize social info

make this into shiny app

```{r}
