---
title: "Adaptive_Adolescence_multi"
author: "Simy"
date: "28/08/2020"
output:
  github_document:
    toc: true
    toc_depth: 2
---

# you have to clean this up Simon

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse,cowplot,matrixcalc,gganimate,ggformula,pracma,doParallel,viridis,adespatial)
```

# Project
Adolescent social sentivity adaptive?
Premise: younger individuals are easier influenced by SI. see Molleman et al 2022 or Ciranka & van den Bos 2022 (hopefully).
So let us explore the kind of envirionment in which higher SI leads to better reward.
I had the idea that if we hide "Rare events" in our task, using social information would make it easier to detect those if individuals have a limited search horizon. As if one sees someone sampling one option often, one believes that the other must´ve found sth worthwile.

# Social

One particular feature about adolescents is that they are sensitive to social information. In order to invesitage how such a sensitivity impacts 1) exploration behavior and 2) encountered outcomes. For this i let _n_ agents perform the task in parallel and introduce a bonus to the choice utilites that depends on how many others have visited this option in the previous trial.

```{r setupsims}
# get sd of whole environemt for normalizing model input
source("models.R")
set.seed(as.numeric(Sys.time()))
loadfromdisk=T
###
###
###
###
### PARAMETERS
###
###
###
#get lambda
#get beta
cntrl_social<-list(
  beta=0,# this scales risk attitude.
  #get tau
  tau=1,
  mu0=100,#exploration bonus
  var0=40,
  #create a parameter vector
  parVec <- c(0.8, 0.8, 1, .0001) ,
  #loop through trials
  out=NULL,
  AllChoices_social=NULL,
  dummy=NULL,
  overallCnt=1,
  dat_social=expand.grid(x1=1:10,x2=1:10),
  
  HowManyOthers=19,
  diminishingSocial=0.8
  # info about the agents
)

```

# load environments that participants saw
and plot them
```{r}

# load the experimental data
explore_data <- read_csv(file = "../data/data_coord.csv")

# load the generated environments
envs_no_gems_list <-
  rjson::fromJSON(file = "../A_GeneratedFiles/environments_no_gem_var25max.json") # max gem value: 250; variance: 25

envs_gems_list <-
  rjson::fromJSON(file = "../A_GeneratedFiles/environments_gem_250_var25max.json") # max gem value: 250; variance: 25

# merge environments together and add identifier

envs_no_gems <- map(envs_no_gems_list, as.data.table)
envs_no_gems <- rbindlist(envs_no_gems) %>% 
  mutate(gems = 0)

envs_gems <- map(envs_gems_list, as.data.table)
envs_gems <- rbindlist(envs_gems) %>% 
  mutate(gems = 1)

#dataframe with environments
envs <- rbind(envs_gems, envs_no_gems)

library(colorspace)
envs%>%
  ggplot(aes(x=x,y=y,fill=Mean))+geom_tile()+
  scale_fill_continuous_divergingx(palette = 'Spectral', mid = 0)+
  #scale_fill_distiller(name="Outcome",palette = "Spectral",trans = "reverse")+
  facet_grid(gems~env_idx,scales="free",labeller = labeller(.rows = label_both, .cols = label_both))+
  theme_minimal(14)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),aspect.ratio = 1)

```

# get the data
Here i load data and retrieve demonstrators for the specific environments. 
```{r}
SI_path="../E_Develop_Social_Version/r"
```

# Simulation
The simulation varies the amount of other agents as well as the weight each agent puts on social information and loops through all of the above generated environments.

```{r}
#HowManyOthers=c(2,3,4,5)
# socialB means social weight
socialB=seq(from=0,to=2,length.out=20)

#otherLoc=0
ntrialss=200
loadfromdisk=F
if (loadfromdisk==F){
  registerDoParallel(detectCores()-5)
  
  Plot_dat_social_All<-foreach(trials=1:ntrialss, .combine='rbind') %dopar%{
    library(dplyr)
    explorations=NULL
    for(i in c(1,4,8,11)){
      for (soc in socialB){
        #for (k in HowManyOthers){
          #update cntrl.
          cntrl_social<-list(
            beta=0,# this scales risk attitude.
            #get tau
            tau=1,
            mu0=100,#exploration bonus
            var0=40,
            #create a parameter vector
            parVec <- c(0.8, 0.8, 1, .0001) ,
            #loop through trials
            out=NULL,
            AllChoices_social=NULL,
            dummy=NULL,
            overallCnt=1,
            dat_social=expand.grid(x1=1:8,x2=1:8),
            
            HowManyOthers=k,
            diminishingSocial=soc
            # info about the agents
          )
          #trials=1
          EnvirionemntAdol=GemEnvs[[i]][,c(1,2)]#subset for one environment
          explorations=rbind(explorations,
                             exploreEnv_Social(explore_func=bayesianMeanTracker,
                                               choiceRule=ucb,
                                               socialfunc=WhereIsEverybody,
                                               env2=EnvirionemntAdol,
                                               env1=EnvirionemntKids,
                                               cntrl=cntrl_social,
                                               trials)%>%
                               mutate(gems=i,socWeight=soc,howMany=k)
                             )
        }
      }
    }
    explorations
  }
  saveRDS(file="../A_GeneratedFiles/simulations/Plot_dat_social_All_04_26_23",object=Plot_dat_social_All)
  # stopCluster(cl)
  
} else{
  Plot_dat_social_AllNew<-readRDS(file="../A_GeneratedFiles/Plot_dat_social_All_04_26_23")
}
```


# results
okay looks like this hidden gems idea wasnt the way to go but there seems to be a natural sweetspot
of social wieght in envirionments that do not have this gem... 
probably has something to do with the spatial structure; kalman agents dont internalize that

# Indivual scale for gems

```{r fig.width=10}
HowManyGems<-Plot_dat_social_AllNew%>%.$gems%>%unique()
HowManyGemsTit<-c(1,4,8,0)
# does how many 1 mean 0???
plotlist=list()
for (i in 1:length(HowManyGems)){
  plotlist[[i]]<-Plot_dat_social_AllNew%>%ungroup()%>%filter(gems==HowManyGems[i])%>%
    dplyr::group_by(howMany,gems,socWeight,trials,iter)%>%
    dplyr::summarise(meanRew=mean(out))%>%
    mutate(found=ifelse(meanRew>200,1,0))%>%
    dplyr::group_by(howMany,gems,socWeight,trials)%>%#mean over iterations
    dplyr::summarise(gemsFoundIter=mean(found))%>%
    dplyr::group_by(howMany,gems,socWeight)%>%#sum over trials
    dplyr::summarise(gemsFoundTrial=sum(gemsFoundIter))%>%
    ggplot(aes(x = socWeight,y=as.factor(howMany),fill=gemsFoundTrial))+
    geom_tile()+
    ggtitle(paste0("n Gems=",HowManyGemsTit[i]))+
    scale_fill_viridis()+theme_bw(14)
}
plot_grid(plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]])
ggsave("environments_SI.png",width=8,height=8)
```

```{r}
Plot_dat_social_AllNew%>%ungroup()%>%#filter(gems==HowManyGems[i])%>%
  dplyr::group_by(howMany,gems,socWeight,trials,iter)%>%
  dplyr::summarise(meanRew=mean(out))%>%
  mutate(found=ifelse(meanRew>200,1,0))%>%
  dplyr::group_by(howMany,gems,socWeight,trials)%>%#mean over iterations
  dplyr::summarise(meanRewT=mean(meanRew))->preprocFig

preprocFig%>%ggplot(aes(x = socWeight,y=meanRewT,color=as.factor(howMany)))+
  geom_point(alpha=0.05)+
  geom_smooth()+
  scale_fill_viridis()+facet_wrap(~gems,scales="free")+theme_bw()
```


# Model with social infuence not on raw but on transforemd utility


# Simulation
The simulation varies the amount of other agents as well as the weight each agent puts on social information and loops through all of the above generated environments.

# smaller environment. randomly hide gems
Here i replace some reward distributions with much higher ones. 
I generate 11 envirionments that contain increasing number of high reward distributions options, from 0 to 10.

```{r}
envirionmentMeanAdol=seq(-50,50,length.out=8)
envirionmentVarianceAdol=rep(c(2,10,15,25),length.out=8)
dat_social=expand.grid(x1=1:8,x2=1:8)

# number of hidden gems
gem_envs=list()
#make gem environments
for (i in 1:6){
  #shuffle environment
  EnvirionemntAdol=expand.grid(Mean=envirionmentMeanAdol,Variance=envirionmentVarianceAdol)%>%
    .[sample(1:nrow(.)),]
  index=sample(x=1:length(EnvirionemntAdol[,1]),size=2)
  Gem=rnorm(2,mean=150,sd=10)
  EnvirionemntAdol[index,1]=Gem
  gem_envs[[i]]=EnvirionemntAdol%>%mutate(env_idx=i)%>%mutate(x=dat_social$x1,y=dat_social$x2)
}# to be nested for SI - no SI

no_gem_envs=list()
#make no gem environment
for (i in 1:6){
  #shuffle environment
  EnvirionemntAdol=expand.grid(Mean=envirionmentMeanAdol,Variance=envirionmentVarianceAdol)%>%
    .[sample(1:nrow(.)),]
  no_gem_envs[[i]]=EnvirionemntAdol%>%mutate(env_idx=i)%>%mutate(x=dat_social$x1,y=dat_social$x2)
}# to be nested for SI - no SI


```




```{r}
loadfromdisk=F

HowManyOthers=c(2,3,4)
socialB=seq(from=0,to=8,length.out=50)

#otherLoc=0
ntrialss=50
if (loadfromdisk==F){
  cores=detectCores()-5
  cl <- makeCluster(cores)  
  registerDoParallel(cl)  
  
  Plot_dat_social_AllProb<-foreach(trials=1:ntrialss, .combine='rbind') %dopar%{
    library(dplyr)
    explorations=NULL
    #for(i in c(4,11)){
    for (soc in socialB){
      for (k in HowManyOthers){
        #update cntrl.
        cntrl_social<-list(
          beta=0,# this scales risk attitude.
          #get tau
          tau=1,
          mu0=50,#exploration bonus
          var0=20,
          #create a parameter vector
          parVec <- c(0.8, 0.8, 1, .0001) ,
          #loop through trials
          out=NULL,
          AllChoices_social=NULL,
          dummy=NULL,
          overallCnt=1,
          dat_social=expand.grid(x1=1:8,x2=1:8),
          
          HowManyOthers=k,
          diminishingSocial=soc
          # info about the agents
        )
        #trials=1
        EnvirionemntAdol=gem_envs[[sample(1:6,1)]][,c(1,2)]#subset for one environment
        explorations=rbind(explorations,exploreEnv_SocialProb(explore_func=bayesianMeanTracker,
                                                              choiceRule=ucb,
                                                              socialfunc=WhereIsEverybody,
                                                              env2=EnvirionemntAdol,
                                                              env1=EnvirionemntKids,
                                                              cntrl=cntrl_social,
                                                              trials)%>%
                             mutate(socWeight=soc,howMany=k))
      }
    }
    explorations
  }
  saveRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_04_26_23.rds",object=Plot_dat_social_AllProb)
  # stopCluster(cl)
} else{
  Plot_dat_social_AllNew<-readRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_04_26_23.rds")
  
}
```


# results
okay looks like this hidden gems idea wasnt the way to go but there seems to be a natural sweetspot
of social wieght in envirionments that do not have this gem... 
probably has something to do with the spatial structure; kalman agents dont internalize that

# Indivual scale for gems

```{r fig.width=10}
# does how many 1 mean 0???
plotlist=list()
#for (i in 1:length(HowManyGems)){
#plotlist[[i]]<-
gems_rew_plot<-Plot_dat_social_AllNew%>%ungroup()%>%#filter(gems==HowManyGems[i])%>%
  dplyr::group_by(howMany,socWeight)%>%
  dplyr::summarise(meanRew=mean(out))%>%
  ggplot(aes(x = socWeight,y=as.factor(howMany),fill=meanRew))+
  geom_tile()+
  ggtitle(paste0("n Gems=2"))+
  scale_fill_viridis()+theme_bw(14)
#}#

unique(Plot_dat_social_AllNew$iter)

#aaaah<-Plot_dat_social_AllNew%>%filter(socWeight %in% socialPruned, iter %in% 1:50)
#saveRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_23_4_22_small.rds",object=aaaah)
```

```{r}
Plot_dat_social_AllNew%>%ungroup()%>%#filter(gems==HowManyGems[i])%>%
  dplyr::group_by(howMany,gems,socWeight,trials,iter)%>%
  dplyr::summarise(meanRew=mean(out))%>%
  mutate(found=ifelse(meanRew>200,1,0))%>%
  dplyr::group_by(howMany,gems,socWeight,trials)%>%#mean over iterations
  dplyr::summarise(meanRewT=mean(meanRew))->preprocFig

preprocFig%>%ggplot(aes(x = socWeight,y=meanRewT,color=as.factor(howMany)))+
  geom_point(alpha=0.05)+
  geom_smooth()+
  scale_fill_viridis()+facet_wrap(~gems,scales="free")+theme_bw()
```
# no gems:

```{r}
HowManyOthers=c(2,3,4)
socialB=seq(from=0,to=8,length.out=50)

#otherLoc=0
ntrialss=50
loadfromdisk=F
if (loadfromdisk==F){
  cores=detectCores()-5
  cl <- makeCluster(cores)  
  registerDoParallel(cl)  
  
  Plot_dat_social_AllProb<-foreach(trials=1:ntrialss, .combine='rbind') %dopar%{
    library(dplyr)
    explorations=NULL
    #for(i in c(4,11)){
    for (soc in socialB){
      for (k in HowManyOthers){
        #update cntrl.
        cntrl_social<-list(
          beta=0,# this scales risk attitude.
          #get tau
          tau=1,
          mu0=50,#exploration bonus
          var0=20,
          #create a parameter vector
          parVec <- c(0.8, 0.8, 1, .0001) ,
          #loop through trials
          out=NULL,
          AllChoices_social=NULL,
          dummy=NULL,
          overallCnt=1,
          dat_social=expand.grid(x1=1:8,x2=1:8),
          
          HowManyOthers=k,
          diminishingSocial=soc
          # info about the agents
        )
        #trials=1
        EnvirionemntAdol=no_gem_envs[[sample(1:6,1)]][,c(1,2)]#subset for one environment
        explorations=rbind(explorations,exploreEnv_SocialProb(explore_func=bayesianMeanTracker,
                                                              choiceRule=ucb,
                                                              socialfunc=WhereIsEverybody,
                                                              env2=EnvirionemntAdol,
                                                              env1=EnvirionemntKids,
                                                              cntrl=cntrl_social,
                                                              trials)%>%
                             mutate(socWeight=soc,howMany=k))
      }
    }
    explorations
  }
  saveRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_NoGem_7_6_22.rds",object=Plot_dat_social_AllProb)
  # stopCluster(cl)
} else{
  #Plot_dat_social_All<-readRDS(file="../A_GeneratedFiles/Plot_dat_social_All.rds")
  Plot_dat_social_all_no_gem<-readRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_NoGem_23_4_22.rds")
  
}
#saveRDS(file="../A_GeneratedFiles/Plot_dat_social_AllProb_NoGem_23_4_22_small.rds",object=aaaaaah2)
```


# Indivual scale for gems

```{r fig.width=10}
# does how many 1 mean 0???
#for (i in 1:length(HowManyGems)){
#plotlist[[i]]<-
no_gems_rew_plot<-Plot_dat_social_all_no_gem%>%ungroup()%>%#filter(gems==HowManyGems[i])%>%
  dplyr::group_by(howMany,socWeight)%>%
  dplyr::summarise(meanRew=mean(out))%>%
  ggplot(aes(x = socWeight,y=as.factor(howMany),fill=meanRew))+
  geom_tile()+
  ggtitle(paste0("n Gems=0"))+
  scale_fill_viridis(option="inferno")+theme_bw(14)
# write environments into jsons
```

```{r}
sims<-plot_grid(no_gems_rew_plot,gems_rew_plot)
ggsave(sims,filename = "simulations.png",height = 5,width = 10)
```

```{r makejsons}
library(jsonlite)
#library(jsontools)

#gems
gem_json1<-gem_envs[[1]]%>%toJSON(dataframe = 'columns')
gem_json2<-gem_envs[[2]]%>%toJSON(dataframe = 'columns')
gem_json3<-gem_envs[[3]]%>%toJSON(dataframe = 'columns')
gem_json4<-gem_envs[[4]]%>%toJSON(dataframe = 'columns')
gem_json5<-gem_envs[[5]]%>%toJSON(dataframe = 'columns')
gem_json6<-gem_envs[[6]]%>%toJSON(dataframe = 'columns')

gem_json <- cat('{"1":', gem_json1, 
                ',"2":', gem_json2, 
                ',"3":', gem_json3,
                ',"4":', gem_json4,
                ',"5":', gem_json5,
                ',"6":', gem_json6,
                '}',
                sep = ' ',
                file = "environments_gem_150_var25max.json"
)

```

```{r}
#no gems
no_gem_json1<-no_gem_envs[[1]]%>%toJSON(dataframe = 'columns')
no_gem_json2<-no_gem_envs[[2]]%>%toJSON(dataframe = 'columns')
no_gem_json3<-no_gem_envs[[3]]%>%toJSON(dataframe = 'columns')
no_gem_json4<-no_gem_envs[[4]]%>%toJSON(dataframe = 'columns')
no_gem_json5<-no_gem_envs[[5]]%>%toJSON(dataframe = 'columns')
no_gem_json6<-no_gem_envs[[6]]%>%toJSON(dataframe = 'columns')

cat('{"1":', no_gem_json1, 
    ',"2":', no_gem_json2, 
    ',"3":', no_gem_json3,
    ',"4":', no_gem_json4,
    ',"5":', no_gem_json5,
    ',"6":', no_gem_json6,
    '}',
    sep = ' ',
    file = "environments_no_gem_var25max.json"
)
```






























































#### Graveyard
```{r}
Plot_dat_social_All%>%ungroup()%>%#filter(gems==11)%>%
  dplyr::group_by(howMany,gems,socWeight)%>%
  dplyr::summarise(meanRew=mean(out))%>%
  ggplot(aes(x = socWeight,y=howMany,fill=meanRew))+
  geom_tile()+
  scale_fill_viridis()+facet_wrap(~gems)
```

# Lets look at SI impact in more detail

```{r}
HowManyOthers=4
socialB=seq(from=0,to=5,length.out=50)
prior=seq(from=-100,to=100,length.out=20)

ntrialss=100
#otherLoc=0
#ntrialss=25
loadfromdisk=F
if (loadfromdisk==F){
  registerDoParallel(detectCores()-5)
  
  Plot_dat_social_All<-foreach(trials=1:ntrialss, .combine='rbind') %dopar%{
    library(dplyr)
    explorations=NULL
    #for(i in 1:11){
    for (i in 1:4){
      for (soc in socialB){
        for (k in prior){
          #update cntrl.
          cntrl_social<-list(
            beta=0,# this scales risk attitude.
            #get tau
            tau=1,
            mu0=k,#exploration bonus
            var0=40,
            #create a parameter vector
            parVec <- c(0.8, 0.8, 1, .0001) ,
            #loop through trials
            out=NULL,
            AllChoices_social=NULL,
            dummy=NULL,
            overallCnt=1,
            dat_social=expand.grid(x1=1:8,x2=1:8),
            
            HowManyOthers=i,
            diminishingSocial=soc
            # info about the agents
          )
          #trials=1
          EnvirionemntAdol=GemEnvs[[11]][,c(1,2)]#subset for one environment
          explorations=rbind(explorations,exploreEnv_Social(explore_func=bayesianMeanTracker,
                                                            choiceRule=ucb,
                                                            socialfunc=WhereIsEverybody,
                                                            env2=EnvirionemntAdol,
                                                            env1=EnvirionemntKids,
                                                            cntrl=cntrl_social,
                                                            trials)%>%
                               mutate(gems=i,socWeight=soc,prior=k,OthersN=i))
        }
      }
    }
    explorations
  }
  saveRDS(file="../A_GeneratedFiles/Plot_dat_social_All_finegraindSOthersN.rds",object=Plot_dat_social_All)
} else{
  Plot_dat_social_All<-readRDS(file="../A_GeneratedFiles/Plot_dat_social_All_finegraindSOthersN.rds")
}
```

```{r}
#this really kills the working memory. do for every iteration
allSummed=NULL
for (i in 1:ntrialss){
  one<-Plot_dat_social_All%>%ungroup()%>%filter(iter==i)%>%
    dplyr::group_by(prior,socWeight)%>%
    dplyr::summarise(meanRew=mean(out),ci=qnorm(0.975)*sd(out)/sqrt(n()))
  
  allSummed<-rbind(allSummed,one)
}
saveRDS(file="../A_GeneratedFiles/Plot_dat_social_All_finegraindSSummed.rds",object=allSummed)
allSummed%>%#filter(prior>80)%>%
  ggplot(aes(x = socWeight,y=meanRew,color=prior))+
  #geom_tile()+
  #geom_point()+
  #geom_errorbar(aes(ymin=meanRew-ci,ymax=meanRew+ci),width=0)+
  #stat_summary(aes(group=prior),geom="line",fun.data="mean_cl_boot")+
  ggtitle("Groupsize 4")+
  stat_smooth(aes(group=prior),fill=NA)+
  stat_smooth()+
  scale_color_viridis()+
  theme_minimal(14)#+theme(panel.grid=element_blank())
#facet_wrap(~gems)

```

# Exploration

Another variable in the model is exploration. we can vary this by setting optimistic or pessimistic priors with more optimism generating the motivation to explore more.

```{r}
```

# stuff to think about:

Currently all agents have the same social sensitivity. we could change that, as in real life this is probably not the case.