---
title: "Adaptive_Adolescence_multi"
author: "Simy"
date: "28/08/2020"
output:
  github_document:
    toc: true
    toc_depth: 2
---

# you have to clean this up Simon

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse,cowplot,matrixcalc,gganimate,ggformula,pracma,doParallel,viridis,adespatial)
```

# Project
Adolescent social sentivity adaptive?
Premise: younger individuals are easier influenced by SI. see Molleman et al 2022 or Ciranka & van den Bos 2022 (hopefully).
So let us explore the kind of envirionment in which higher SI leads to better reward.
I had the idea that if we hide "Rare events" in our task, using social information would make it easier to detect those if individuals have a limited search horizon. As if one sees someone sampling one option often, one believes that the other must´ve found sth worthwile.

# Social

One particular feature about adolescents is that they are sensitive to social information. In order to invesitage how such a sensitivity impacts 1) exploration behavior and 2) encountered outcomes. For this i let _n_ agents perform the task in parallel and introduce a bonus to the choice utilites that depends on how many others have visited this option in the previous trial.

```{r setupsims}
# get sd of whole environemt for normalizing model input
source("models.R")
set.seed(as.numeric(Sys.time()))
loadfromdisk=T
###
###
###
###
### PARAMETERS
###
###
###
#get lambda
#get beta
cntrl_social<-list(
  beta=0,# this scales risk attitude.
  #get tau
  tau=1,
  mu0=0,#exploration bonus
  var0=40,
  #create a parameter vector
  parVec <- c(0.8, 0.8, 1, .0001) ,
  #loop through trials
  out=NULL,
  AllChoices_social=NULL,
  dummy=NULL,
  overallCnt=1,
  dat_social=expand.grid(x1=1:10,x2=1:10),
  
  HowManyOthers=19,
  diminishingSocial=0.8
  # info about the agents
)

```

# load environments that participants saw
and plot them
```{r}

# load the experimental data
explore_data <- read_csv(file = "../data/data_coord.csv")

# load the generated environments
envs_no_gems_list <-
  rjson::fromJSON(file = "../A_GeneratedFiles/environments_no_gem_var25max.json") # max gem value: 250; variance: 25

envs_gems_list <-
  rjson::fromJSON(file = "../A_GeneratedFiles/environments_gem_250_var25max.json") # max gem value: 250; variance: 25

# merge environments together and add identifier

envs_no_gems <- map(envs_no_gems_list, as.data.table)
envs_no_gems <- rbindlist(envs_no_gems) %>% 
  mutate(gems = 0)

envs_gems <- map(envs_gems_list, as.data.table)
envs_gems <- rbindlist(envs_gems) %>%
  mutate(env_idx=env_idx+6)%>%
  mutate(gems = 1)

#dataframe with environments
envs <- rbind(envs_gems, envs_no_gems)

library(colorspace)
envs%>%
  ggplot(aes(x=x,y=y,fill=Mean))+geom_tile()+
  scale_fill_continuous_divergingx(palette = 'Spectral', mid = 0)+
  #scale_fill_distiller(name="Outcome",palette = "Spectral",trans = "reverse")+
  facet_wrap(~env_idx,scales="free")+#labeller = labeller(.rows = label_both, .cols = label_both))+
  theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),aspect.ratio = 1)

```

# get the data
Here i load data and retrieve demonstrators for the specific environments and put them into a tidy dataframe. 
```{r}
SI_path="../E_Develop_Social_Version/rounds_social_info/1_peer/social_info_json/"

# load jsons with the selected social information and concat them in dataframe.
# doublechek if the sequence is correct (how?)
# figure out which are supposed to be rotaded. makes no difference for the simulation
demonstrators<-list.files(SI_path)%>%
  purrr::map_dfr(.,~{
    tibble(
      choices = read_json(paste0(SI_path,.))$cells%>%unlist(),
      env = read_json(paste0(SI_path,.))$envNr%>%unlist(),
      player = read_json(paste0(SI_path,.))$roundNr%>%unlist(),
      gem = read_json(paste0(SI_path,.))$gempresent%>%unlist()
    )
  }
)
no_gem=c(800,921,254,1599,1899,408)
gem_not_found<-c(1650,  504,  376,  868,  332, 1434)
gem_found<-c(905, 1625, 1912,  335,  343,  795)
never_exploit<-c(838, 2195, 1177, 1244,  468, 1639)

demonstrators<-demonstrators%>%mutate(
  type = case_when(player %in% no_gem ~ "no_gem",
                 player %in% gem_not_found ~ "gem_not_found",
                 player %in% gem_found ~ "gem_found",
                 player %in% never_exploit ~ "never_exploit")
  )

```

# Simulation
The simulation varies the amount of other agents as well as the weight each agent puts on social information and loops through all of the above generated environments.

```{r}
#HowManyOthers=c(2,3,4,5)
# socialB means social weight
social_weights=seq(from=0,to=10,length.out=5)
#otherLoc=0
others<-unique(demonstrators$player)
loadfromdisk=F
repetitions=40
if (loadfromdisk==F){
  registerDoParallel(detectCores()-5)
  
  Plot_dat_social_All<-foreach(rep=1:repetitions, .combine='rbind') %dopar%{
    library(dplyr)
    explorations=NULL
    for(oth in others){
      for (soc_w in social_weights){
        #for (k in HowManyOthers){
        indx=demonstrators%>%filter(player==oth)%>%pull(env)%>%unique()# find environment of demonstrator
        demo_type=demonstrators%>%filter(player==oth)%>%pull(type)%>%unique()
        demonst_indx=demonstrators%>%filter(player==oth)%>%pull(choices)#%>%unique()
        demonst_indx[demonst_indx == 64]<-63
        demonst_indx=demonst_indx+1
        environment=envs%>%filter(env_idx==indx)#subset for the environment seen by the demonstrator
        #update cntrl.
        # list of stuff that is unpacked in the simulation function
        cntrl_social<-list(
          beta=0,# this scales risk attitude.
          #get tau
          tau=1,
          mu0=0,#exploration bonus
          var0=40,
          #create a parameter vector
          parVec <- c(0.8, 0.8, 1, .0001) ,
          #loop through trials
          out=NULL,
          social_choices=demonst_indx,
          dummy=NULL,
          overallCnt=1,
          dat_social=expand.grid(x1=1:8,x2=1:8),
         # HowManyOthers=k,
          social_weight=soc_w
          # info about the agents
        )
        #trials=1

        explorations=rbind(explorations,
                           explore_env_social(explore_func=bayesianMeanTracker,
                                             choiceRule=ucb,
                                             env=environment,
                                             cntrl=cntrl_social,
                                             rep)%>%
                             mutate(soc_w=soc_w,demonstrator=oth,repetition=rep,env=indx,type=demo_type)
        )
    }
  }
  explorations
}
saveRDS(file="../A_GeneratedFiles/simulations/soc_sims_selected_demonstrator.rds",object=Plot_dat_social_All)
# stopCluster(cl)

} else{
  Plot_dat_social_AllNew<-readRDS(file="../A_GeneratedFiles/soc_sims_selected_demonstrator.rds")
}
```


# visualize sims

```{r}

```



