```{r echo=FALSE, warning=FALSE}

pacman::p_load(tidyverse, rjson, data.table, gghalves, here, lmerTest, infer)
'%!in%' <- function(x,y)!('%in%'(x,y))
```

```{r load data, echo=FALSE, warning=FALSE, message=FALSE }

all_data <- read_csv(file = paste0(here(), "/data/social/data_social_all_participants.csv")) 


### move this to cleaning script
  
all_data %>% 
  filter(demo_type == "gem_found") %>% 
  ggplot(aes(x = gem_found_social_info, fill = factor(soc_info_round))) + 
  geom_histogram()
 
  all_data <-
  all_data %>%   ungroup() %>%
  group_by(unique_rounds) %>% 
  mutate(remain_gem = case_when(
      trial > round_gem_found &
        cell == gem_cell ~ 1,
      trial > round_gem_found &
        cell != gem_cell ~ 0,
      TRUE ~ NA
    )
  ) %>%   ungroup()  


problem_data <- all_data %>%
 #filter(remain_gem != 1) %>%  
  filter(gem_found == 1 & trial > round_gem_found) %>%
  ungroup() %>% 
  group_by(uniqueID, round) %>% 
  mutate(n_explore_after_gem = length(unique(cell)),                                            remaining_trials = 25 - round_gem_found,
         n_clicks =  n_explore_after_gem )

problem_people <- problem_data %>% 
  select(uniqueID, group, round, n_explore_after_gem) %>% 
  filter(n_explore_after_gem > 3) %>% 
  distinct() %>% 
  group_by(uniqueID, group) %>% 
  summarise(n = n())

problem_adults <- problem_people %>% 
  filter(group == 'adults') 

problem_data %>%
  select(unique_rounds, group, n_explore_after_gem) %>% 
  filter(n_explore_after_gem > 3) %>% 
  distinct() %>% 
  select(unique_rounds) %>% 
  pull() -> problem_rounds


all_data <- all_data %>% 
  ungroup() %>% 
  group_by(soc_info_round) %>% 
  mutate(gem_found_social_info = ifelse(soc_info_round == 335, 11,
                                  ifelse(soc_info_round == 795, 16,
                                        ifelse(soc_info_round == 1625, 6,
                                               ifelse(soc_info_round == 1912, 14,
                                                      ifelse(soc_info_round == 905, 8,
                                                             ifelse(soc_info_round == 343, 17, NA)))))),
         gem_found_how = ifelse(round_gem_found < gem_found_social_info, 'alone', ifelse(round_gem_found >= gem_found_social_info, 'copier', NA))) %>%   filter(unique_rounds %!in% problem_rounds)

```

## Demographics

sample size and age distribution

```{r}

all_data %>% 
  ungroup() %>% 
  select(age, uniqueID) %>% 
  distinct() %>% 
  ggplot()+
  geom_histogram(aes(x=age))

all_data %>% 
  ungroup() %>% 
  select(uniqueID, group) %>% 
  distinct() %>% 
  ggplot()+
  geom_bar(aes(x = group))

```


# Behavior

## Task sanity checks

### n of boxes open

Result 1: adults open slightly more boxes

```{r warning=FALSE, echo=FALSE,  message=FALSE}

boxes_data <- 
all_data %>% 
  group_by(round, uniqueID, gempresent, group, demo_type) %>% 
  summarise(boxes_opened = n_distinct(cells)) 

summary(lmer(boxes_opened ~ group * demo_type + (1|uniqueID), data = boxes_data ))

all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(cells)) %>%
  ggplot(aes(x = factor(gempresent), y = boxes_opened)) +
  geom_boxplot(aes(fill = factor(gem_found))) +
  scale_fill_brewer(name = "gem found", label = c("no", "yes")) +
  scale_x_discrete(label = c("no", "yes")) +
  labs(x = "gem present", y = 'n of different boxes') +
  theme_bw(base_size = 20) +  facet_grid( ~ group)



all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(cells)) %>%
  ggplot(aes(x = factor(round), y = boxes_opened)) +
  geom_boxplot(aes(fill = factor(gem_found))) +
  scale_fill_brewer(name = "gem found", label = c("no", "yes")) +
 # scale_x_discrete(label = c("no", "yes")) +
  labs(x = "gem present", y = 'n of different boxes') +
  theme_bw(base_size = 20) +  facet_grid( ~ group+gempresent)

all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(cells)) %>% 
lmer(boxes_opened ~ group * round * gem_found+ (1|uniqueID), data = .) -> reg

summary(reg)



```


When do adults find gems?

later then adolescents

```{r}
# 
# all_data %>% 
#   filter(gem_found == 1) %>% 
#   group_by(uniqueID, group, demo_type) %>% 
#   summarise(round_gem_found = mean(round_gem_found, na.omit = TRUE)) %>% 
#   ggplot()+
#   geom_boxplot(aes(x = group, y = round_gem_found, fill = demo_type))
# 
# 
# summary(lmer(round_gem_found ~ group * demo_type  + (1|player), data =))
# 

```


people open less boxes when gem is found early
also people open fewer boxes when demonstrator finds gem

```{r warning=FALSE, echo=FALSE,  message=FALSE}

all_data %>% 
  filter(gem_found==1) %>% 
  group_by(round, uniqueID, gempresent, gem_found, group) %>% 
  summarise(boxes_opened = n_distinct(cells),
            round_gem_found=round_gem_found, 
            demo_type = demo_type) %>% 
  ggplot(aes(x = factor(round_gem_found), y = boxes_opened, color = demo_type)) +
  stat_summary()+
  #scale_fill_brewer(name = "gem found", label = c("no", "yes"))+
 # scale_x_discrete(label = c("no", "yes")) +
  labs(x = "trial gem found", y = 'n of different boxes') +
  theme_bw(base_size = 15) +
  facet_wrap(~group)
  
  ```

## Performance

### Distribution of points scored

```{r warning=FALSE, echo=FALSE,  message=FALSE}
# absolute points

all_data %>% 
  group_by(uniqueID, gempresent, points, group) %>% 
  distinct() %>% 
  ggplot() +
  geom_histogram(aes( x = points, y = stat(density), fill = gemlabel), binwidth = 10) +
  geom_vline(xintercept = 0, lty = 1, size = 1.5, color = 'red') + 
  #geom_half_point(aes(x = factor(gempresent), y = points), alpha = 0.02) +
  theme_bw(base_size = 20) +
  labs(title = 'points scored per click', y = 'proportion') +
  (facet_grid(~group))

```

### How are gem found?

3/4 times, by copying, some times independentely

```{r}

all_data %>% 
  select(gem_found_how, unique_rounds) %>% 
  distinct() %>% 
  filter(!is.na(gem_found_how)) %>% 
  ggplot() +
  geom_bar(aes(x = gem_found_how))

```


### Points score over time

adolescents score more points in gem environments

```{r echo=FALSE, message=FALSE}

only_good_players <- 
all_data %>% 
  filter(unique_rounds %!in% problem_rounds) 


only_good_players %>%
  group_by(uniqueID, trial, group) %>%
  ggplot(aes(x = trial, y = points, color = factor(demo_type), shape = group)) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  scale_color_brewer(type = "qual", palette = 2, name = "gem found", label = c("no", "yes"))+
  facet_wrap( ~ gem_found) +
  labs(title = 'avg points per trial') +
  theme_bw(base_size = 20) 

only_good_players %>%
  group_by(uniqueID, trial, group) %>%
  ggplot(aes(x = group, y = tot_points, color = factor(demo_type), shape = group)) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  #scale_color_brewer(type = "qual", palette = 2, name = "gem found", label = c("no", "yes"))+
  facet_grid( ~ demo_type) +
  labs(title = 'avg points per environment') +
  theme_bw(base_size = 20) 


```

adolescents seem to score more points on average when demonstrators find gems

```{r echo=FALSE, message=FALSE}

only_good_players %>%
  filter(gempresent == 1 ) %>% 
  group_by(uniqueID, trial) %>%
  ggplot(aes(x = trial, y = points, color = group, shape = factor(demo_type))) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  scale_color_brewer(type = "qual", palette = 2, name = "demonnstrator type")+
  #facet_wrap( ~ group) +
  labs(title = 'avg points per trial in gem environments') +
  theme_bw(base_size = 15)

```

### n of gems found

adults find slightly more gems on average

```{r echo=FALSE, message=FALSE, warning=FALSE}

only_good_players %>% 
  filter(gempresent == 1) %>% 
  group_by(uniqueID, round, group) %>% 
  summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
  group_by(uniqueID, group) %>% 
  summarise(n_gems = sum(gem_found)) %>% 
  infer::t_test(n_gems ~ group)
  

# mean_gems_by_groups <- 
# all_data %>% 
#   filter(gempresent == 1) %>% 
#   group_by(uniqueID, round, group) %>% 
#   summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
#   group_by(uniqueID, group) %>% 
#   summarise(n_gems = sum(gem_found)) %>% 
#   group_by(group) %>% 
#   summarise(mean_gems = mean(n_gems))
# 
# 
# 
# all_data %>% 
#   filter(gempresent == 1) %>% 
#   group_by(uniqueID, round, group) %>% 
#   summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
#   group_by(uniqueID, group) %>% 
#   summarise(n_gems = sum(gem_found)) %>% 
#   ggplot() +
#   geom_histogram(aes(x =  n_gems, y =stat(density)), binwidth = 1, fill = "black")+
#   geom_vline(data = mean_gems_by_groups, aes(xintercept = (mean_gems))) +
#   theme_bw(base_size = 20) +
#   labs(x = 'n of environments in which a gem was found') +
#   facet_wrap(~group)
# 

only_good_players %>% 
  filter(gempresent == 1) %>% 
  group_by(uniqueID, round, group) %>% 
  summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
  group_by(uniqueID, group) %>% 
  summarise(n_gems = sum(gem_found)) %>% 
  ggplot() +
  geom_boxplot(aes(x =  n_gems/8, y = group, fill = group) ) +
  stat_summary(aes(x =  n_gems/8, y = group, fill = group)) +
  labs(title = 'gem found by group', x = 'proportion of gem found') +
  guides(fill = FALSE)


```

most participants find gems in half of the environments that contain them (4 out 8), and some more than that.

## explore exploit after gem or not

```{r echo=FALSE, message=FALSE, warning=FALSE}
# 
# 
# explore_exploit <- 

only_good_players %>%
  group_by(uniqueID, group) %>%
  mutate(exploit = ifelse(lead(cells) == cells, 1, 0),
         explore = ifelse(lead(cells) != cells, 1, 0)) %>%
  mutate(out_cat = case_when(points > 150 ~ 1,
                             points < 0 ~ 3,
                             TRUE ~ 2)) %>% pivot_longer(cols = c(exploit, explore), names_to = "explore_exploit") %>%
  ggplot(aes(
    x = out_cat,
    y = value,
    color = explore_exploit,
    shape = group
  )) +
  stat_summary(size = 1) +
  stat_summary(geom = "line") +
  scale_y_continuous(name = "proportion") +
  scale_x_continuous(
    name = "reward type",
    breaks = c(1, 2, 3),
    labels = c("gem", "no gem", "loss")
  ) +
  #scale_color_brewer(type = 'qual', palette = 6, name = 'explore/exploit')+
  scale_color_manual(values = c("#FFC20A", "#0C7BDC"), name = 'explore/exploit' )+
  theme_bw(15) +
  facet_wrap(~gemlabel)+
 # guides(shape = FALSE)+
    theme(axis.text=element_text(size=20))+
  labs(title = 'explore or exploit by reward type')

# 
#   ggsave(filename = 'explore_exploit.png', explore_exploit, width = 12.5,height=6  )


    
```

## Social behavior

also add age here

```{r echo=FALSE, message=FALSE, warning=FALSE}


only_good_players %>% 
  filter(!is.na(demo_type)) %>% 
  mutate(social_info_use_num = ifelse(social_info_use == "copy", 1, 0)) %>% 
  group_by(uniqueID, round,group) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  select(unique_rounds, n, demo_type) %>% 
  distinct() %>% 
  group_by(uniqueID,demo_type,group) %>% 
  summarize(mean_copy = mean(n),
            demo_type = demo_type) %>% 
  ggplot() +
  geom_histogram(aes(x=mean_copy, y = stat(density), group = demo_type, fill = demo_type), binwidth = 1) +
  facet_grid(~demo_type+group) +
  labs(title = 'average copy per participant in each treatment') +
  theme_bw(15)


```

```{r echo=FALSE, message=FALSE, warning=FALSE}

points_by_treat <- all_data %>% 
  mutate(social_info_use_num = ifelse(social_info_use=="ignore", 0, 1)) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  ggplot()+
  stat_summary(aes (x = n, y = tot_points, color = factor(gem_found, levels = c(1,0)), shape = group)) +
  geom_smooth(aes (x = n, y = tot_points),method = "lm")+
  facet_wrap(~demo_type, scales = 'free')+  
  theme_bw(base_size = 15) +
  scale_color_brewer(type = "qual",palette = 2, name = "gem found", label = c("yes", "no"))+
  labs(x = 'n of rounds copying social information', y='total points', title = 'total points by frequency of social info use') +
    theme_bw(15)+
  theme(axis.text=element_text(size=15))

points_by_treat
  

# ggsave(filename = 'points_by_treat.png', points_by_treat, width = 14,height=6  )

```

do adults use more social info?

```{r}


only_good_players %>%
  ggplot() +
  geom_bar(aes(x = factor(trial),  fill = social_info_use), position = "fill")+
  facet_grid(~group + demo_type)

```


When are gems found

```{r}

  all_data %>%
  filter(gempresent == 1) %>%
  ungroup %>%
  group_by(demo_type, gem_found, group) %>%
  select(uniqueID, round, gem_found, round_gem_found, gempresent, group) %>%
  distinct() %>%
  select(gem_found, round_gem_found, group) %>%
  summarise(mean_round_found = mean(round_gem_found, na.rm = TRUE),
            n = n()) %>%
  ungroup() %>%
  group_by(demo_type, group) %>%
  mutate(freq = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(
    x = demo_type,
    y = freq,
    fill = factor(gem_found, levels = c(1,0))
  )) +
  scale_fill_brewer(
    type = "qual",
    palette = 7,
    name = "",
    label = c("yes", "no")
  ) +
  labs(x = 'social information type', title = 'did players find gems?', y = 'proportion of rounds') +
    theme_classic(base_size = 15) +
    theme(axis.text = element_text(size = 10)) +
    facet_wrap( ~ group)
  

  #ggsave(filename = 'gem_found.png', gem_found, width = 8,height=6  )
  
```


copy frequency by treatment and succes


```{r}

## find the same gem of 

 only_good_players %>% 
  mutate(social_info_use_num = ifelse(social_info_use == "copy", 1, 0)) %>% 
  group_by(unique_rounds) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  ungroup() %>% 
  select(uniqueID, n, demo_type, gem_found, group) %>% 
  distinct() %>% 
  group_by(uniqueID,demo_type,group, gem_found) %>% 
#  reframe(mean_copy = mean(n)) %>% 
 # distinct() %>% 
  ggplot() +
  stat_summary(aes(x = demo_type, y = n, color = group)) +
  facet_wrap(~gem_found)


only_good_players %>% group_by(demo_type, uniqueID, round, group, gem_found, age) %>%
filter(social_info_use == "copy") %>%
  count(social_info_use) %>%
  ggplot(aes(
    x = demo_type,
    y = n,
    shape = social_info_use,
    color = group
  )) +
  stat_summary() +
  geom_hline(yintercept = 25 / 64,
             linetype = "dotted",
             color = "red") +
  # facet_wrap(.~group)+
  theme_minimal(14) +
  facet_wrap(. ~ gem_found, labeller = label_both) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


### when are gem found

```{r}

hist(all_data$round_gem_found)

all_data %>% 
  filter(gem_found==1 & gem_found_how == 'copier') %>% 
  select(round_gem_found, group, demo_type, uniqueID) %>% 
  group_by(uniqueID) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = round_gem_found, fill = group)) + 
  geom_half_boxplot()+
  geom_half_point(alpha = 0.1)+
  stat_summary(color = 'red')+
  facet_wrap(~demo_type)

all_data %>% 
  filter(gem_found==1 & gem_found_how == 'copier') %>%
    select(round_gem_found, group, demo_type, uniqueID) %>% 
    group_by(uniqueID) %>% 
distinct() %>% 
  lm(round_gem_found ~ group  , data = .) -> model_when_gem

summary(model_when_gem)
  
```

### people don't copy exploit?

half of the adults don't exploit until the end.

```{r merge datasets, warning=FALSE, echo=FALSE, message=FALSE}

 

hist(problem_adults$n)


problem_data %>%    select(unique_rounds, n_clicks, round_gem_found, demo_type, group) %>%    distinct() %>%    ggplot() +   geom_histogram(aes(x = n_clicks, y = stat(density), group = group, fill =                                                                                                                                     factor(demo_type)), binwidth = 1) +   geom_vline(aes(xintercept = mean(n_clicks))) +   theme_bw(base_size = 15) +   labs(x = 'proportion of explore clicks after gem',         y = 'n of unique rounds (1 environment)', title = "behavior after gem was found") +    facet_wrap(~ group)



explore_after_gem %>%    filter(remain_gem != 1) %>%    group_by(unique_rounds, round_gem_found) %>%    summarise(n = n())

all_data %>%    ungroup() %>%    select(unique_rounds, gempresent, gem_found) %>%    group_by(gempresent, gem_found) %>%    distinct() %>%    summarise(n = n())
```

# 
