################################################################# 

## Behavioral analyses main script

################################################################# 

```{r echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

## load packages @andrea implement pck_mgmt script
pacman::p_load(tidyverse,
               rjson,
               data.table,
               gghalves,
               here,
               lme4,
               lmerTest,
               broom.mixed,
               infer,
               ggthemes,
               sjPlot)

'%!in%' <- function(x,y)!('%in%'(x,y))

options(scipen = 999,digits = 4)
```

```{r load data, echo=FALSE, warning=FALSE, message=FALSE }

## load data
#all_data <- read_csv(file = paste0(here(), "/data/social/data_social_all_participants.csv")) 
all_data <- read_csv(file = paste0(here(), "/data/social/data_social_all_participants_07-2024.csv"))

```

## Demographics

sample size and age distribution

```{r sample, warning=FALSE, message=FALSE}

## age distribution
all_data %>% 
  ungroup() %>% 
  select(uniqueID, group) %>% 
  group_by( group) %>% 
  distinct() %>%
  count()

all_data %>% 
  ungroup() %>% 
  select(uniqueID, age, group) %>% 
  distinct() %>% 
  ggplot() +
  geom_histogram(aes(x = age, fill = group), binwidth = 1) +
  theme_base(base_size = 15)

## count by group
all_data %>%
  ungroup() %>% 
  select(uniqueID, group) %>% 
  distinct() %>% 
  ggplot()+
  geom_bar(aes(x = group))

```

# Behavior

## Task sanity checks

### exploration: n of boxes open

Result 1: adults open slightly more boxes

```{r explorative-behavior, warning=FALSE, echo=FALSE,  message=FALSE}

## create dataset
boxes_data <- 
all_data %>% 
  group_by(round, uniqueID, gempresent, group, demo_type) %>% 
  summarise(boxes_opened = n_distinct(choice)) ## n of unique choice = n of different boxes opened

## quick regression if n of boxes opened ~ group and demo type
sjPlot::tab_model(glmer(boxes_opened ~ group * demo_type + (1|uniqueID), family = poisson, data = boxes_data))

## plot: n unique boxes by group and gem condition
all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(choice)) %>%
  ggplot(aes(x = factor(gempresent), y = boxes_opened)) +
  geom_boxplot(aes(fill = factor(gem_found))) +
  scale_fill_brewer(name = "gem found", label = c("no", "yes")) +
  scale_x_discrete(label = c("no", "yes")) +
  labs(x = "gem present", y = 'n of different boxes') +
  theme_bw(base_size = 20) +  facet_grid( ~ group)

## plot mean boxes open before and after finding gem
```

### boxes open by round

people open less boxes when gem is found early also people open fewer boxes when demonstrator finds gem

```{r boxes open by gem outcome, warning=FALSE, echo=FALSE,  message=FALSE}

all_data %>% 
  filter(gem_found==1) %>% 
  group_by(round, uniqueID, gempresent, gem_found, group) %>% 
  summarise(boxes_opened = n_distinct(choice),
            round_gem_found=round_gem_found, 
            demo_type = demo_type) %>% 
  ggplot(aes(x = factor(round_gem_found), y = boxes_opened, color = demo_type)) +
  stat_summary()+
  #scale_fill_brewer(name = "gem found", label = c("no", "yes"))+
 # scale_x_discrete(label = c("no", "yes")) +
  labs(x = "trial gem found", y = 'n of different boxes') +
  theme_base(base_size = 15) +
  facet_wrap(~group)
  
```

### Does exploration decrease over time?

```{r task fatigue, warning=FALSE, message=FALSE}

## does exploration decrease over rounds?
all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(choice)) %>%
  ggplot(aes(x = factor(round), y = boxes_opened)) +
  geom_boxplot(aes(fill = factor(gem_found))) +
  scale_fill_brewer(name = "gem found", label = c("no", "yes")) +
 # scale_x_discrete(label = c("no", "yes")) +
  labs(x = "gem present", y = 'n of different boxes') +
  theme_bw(base_size = 20) +  facet_grid( ~ group+gempresent)

## regression
all_data %>%
  group_by(round, uniqueID, gempresent, gem_found, group) %>%
  summarise(boxes_opened = n_distinct(choice)) %>% 
glm(boxes_opened ~ group * round * gem_found, family = poisson, data = .) -> regression_fatigue

tab_model(regression_fatigue)

```

### social info sanity check, at what rounds are gem found by demonstrator

```{r n of rounds by condition, warning=FALSE, message=FALSE}

## plot how many final round for any treatment (i.e. type of demonstrator) were there after cleaning the data
all_data %>% 
  filter(demo_type == "gem_found") %>% 
  ggplot(aes(x = gem_found_social_info, fill = factor(soc_info_round))) + 
  geom_histogram()

```

When do adults find gems? later then adolescents

```{r gem found when bry group, warning=FALSE, message=FALSE}

## basic plot
all_data %>%
  filter(gem_found == 1) %>%
  group_by(uniqueID, group, demo_type) %>%
  summarise(round_gem_found = mean(round_gem_found, na.omit = TRUE)) %>%
  ggplot()+
  geom_boxplot(aes(x = group, y = round_gem_found, fill = demo_type)) + 
  theme_base(base_size = 15)

## poisson regression: round when gem was found by group and treatment (demonstrator type)
tab_model(glmer(round_gem_found ~ group * demo_type  + (1|player), family = poisson(), data = all_data))



## condition on round where demonstrator finds the gem first
all_data %>% 
  filter(gem_found == 1 & gem_found_how == 'copier') %>% 
  select(round_gem_found, group, demo_type, uniqueID) %>% 
  group_by(uniqueID) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = round_gem_found, fill = group)) + 
  geom_half_boxplot(errorbar.draw = FALSE)+
  geom_half_point(aes(color = group), alpha = 0.2,
              )+
  stat_summary(   geom = "point",
                  shape =23,
                  size = 2,
                  stroke = 1,
                  color = "black",
                  fill = "white")+
  scale_color_brewer(
    type = "qual",
    palette = 2) +
  scale_fill_brewer(
    type = "qual",
    palette = 2) +
  labs(title = '',
       y = 'clicks before gem is found') +
facet_wrap(~demo_type) +
  theme_base(base_size = 20) +
  guides(color = FALSE, fill = FALSE)


```

How do people find gems

## Performance

### Distribution of points scored

```{r distribution of points, warning=FALSE, echo=FALSE,  message=FALSE}
# absolute points

#@andrea: height of distribution

all_data %>% 
  group_by(uniqueID, gempresent, points) %>% 
  distinct() %>% 
  ggplot(aes()) +
    geom_histogram(aes( x = points, y = stat(density), color = gemlabel),  position = "identity", binwidth = 10, fill = "white", alpha = 0) +
  geom_vline(xintercept = 0, lty = 1, size = 1.5, color = 'red') + 
  #geom_half_point(aes(x = factor(gempresent), y = points), alpha = 0.02) +
  theme_bw(base_size = 20) +
  labs(title = 'points scored per click', y = 'proportion') +
  facet_grid(~group)

```

### Total points scored

```{r total points scored, warning=FALSE, message=FALSE}
all_data %>%
  group_by(uniqueID, group) %>%
  select(uniqueID, group, demo_quality, tot_points, gem_found) %>%
  distinct() %>%
  ggplot(aes(
    x = group,
    y = tot_points,
    #color = factor(gem_found),
    shape = group
  )) +
  # geom_signif(
  #   comparisons = list(c("adolescents", "adults")),
  #   map_signif_level = TRUE, y_position = 1050,tip_length = 0, textsize = 20, vjust = 500, )+
  stat_summary(size = 1, lwd = 1) +
  # scale_color_brewer(
  #   type = "qual",
  #   palette = 2,
  #   name = "quality of demonstrator",
  #   label = c("finds a gem", "settles for good option", "explores until the end")
  # ) +
  # facet_grid( ~ gem_found) +
  #ylim(c(500,1400))+
  labs(title = 'Adolescents score more points than adults',
       #subtitle = 'especially g',
       y = 'average points per round') +
  theme_base(base_size = 20)+
  # facet_grid( ~ demo_quality) +
  guides(shape = FALSE)

```

### How are gem found?

3/4 times, by copying, some times independently

```{r gem by strategy}

all_data %>% 
  select(gem_found_how, unique_rounds, demo_quality_f, age_f) %>% 
  distinct() %>% 
  filter(!is.na(gem_found_how)) %>% 
  ggplot() +
  geom_bar(aes(x = demo_quality_f, fill = gem_found_how)) 
 
  

```

### Points score over time

adolescents score more points in gem environments

```{r points by trial, echo=FALSE, message=FALSE}
all_data %>%
  group_by(uniqueID, trial, group) %>%
  ggplot(aes(x = trial, y = points, color = factor(gem_found), shape = group)) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  scale_color_brewer(type = "qual", palette = 2, name = "gem found", label = c("no", "yes"))+
 # facet_wrap( ~ gem_found) +
  labs(title = 'average points per trial') +
  theme_bw(base_size = 20)



```


```{r points by envir, echo=FALSE, message=FALSE}
all_data %>%
  group_by(uniqueID, trial, group) %>%
  ggplot(aes(x = group, y = tot_points, color = factor(demo_type), shape = group)) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  #scale_color_brewer(type = "qual", palette = 2, name = "gem found", label = c("no", "yes"))+
  facet_grid( ~ demo_type) +
  labs(title = 'average points per environment') +
  theme_bw(base_size = 20) 


```

adolescents seem to score more points on average when demonstrators find gems

```{r points by demonstrator, echo=FALSE, message=FALSE}

all_data %>%
  filter(gempresent == 1 ) %>% 
  group_by(uniqueID, trial) %>%
  ggplot(aes(x = trial, y = points, color = group, shape = factor(demo_type))) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  scale_color_brewer(type = "qual", palette = 2, name = "demonnstrator type")+
  #facet_wrap( ~ group) +
  labs(title = 'avg points per trial in gem environments') +
  theme_bw(base_size = 15)


```

```{r}

all_data %>%
  #filter(gempresent == 1 ) %>% 
  group_by(uniqueID, trial) %>%
  ggplot(aes(x = trial, y = points, color = group, shape = factor(demo_type))) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  scale_color_brewer(type = "qual", palette = 2, name = "demonnstrator type")+
  #facet_wrap( ~ group) +
  labs(title = 'avg points per trial in gem environments') +
  theme_bw(base_size = 15)


```


```{r points by age group}
all_data %>% 
  ggplot()+
  geom_bar(aes(x = demo_quality))

all_data %>% 
   group_by(uniqueID, group) %>% 
  select(uniqueID, group, demo_quality, tot_points) %>%
  distinct() %>% 
  ggplot(aes(x = group, y = tot_points, color = demo_quality, shape = group)) +
  stat_summary() +
  theme_minimal(base_size = 15) +
  #scale_color_brewer(type = "qual", palette = 2, name = "gem found", label = c("no", "yes"))+
 # facet_grid( ~ demo_quality) +
  labs(title = 'Adolescents score more points than adults',
       subtitle = '',
       y = 'average points per round') +
  theme_bw(base_size = 20)
```


```{r points by age group regression}

interaction_data <- all_data %>% 
ungroup() %>% 
    select(uniqueID, group, demo_quality, tot_points) %>%
  distinct() 


# summary(aov(tot_points ~ demo_quality  * group , data = interaction_data ))
# 

## points scored by group and demonstrator type
interaction_model <-
  brms::brm(tot_points ~ demo_quality * group + (1 |
                                                   uniqueID), data = interaction_data)

summary(interaction)



```

### n of gems found

adults find slightly more gems on average

```{r gem found by group, echo=FALSE, message=FALSE, warning=FALSE}

all_data %>% 
  filter(gempresent == 1) %>% 
  group_by(uniqueID, round, group) %>% 
  summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
  group_by(uniqueID, group) %>% 
  summarise(n_gems = sum(gem_found)) %>% 
  infer::t_test(n_gems ~ group)

all_data %>% 
  filter(gempresent == 1) %>% 
  group_by(uniqueID, round, group, demo_type) %>% 
  summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
  group_by(uniqueID, group,demo_type) %>% 
  summarise(n_gems = sum(gem_found)) %>%
  ungroup()%>%
  group_by(demo_type)%>%
  group_split() -> data_t_test

## 
  infer::t_test(x = data_t_test[[1]], n_gems ~ group )
  infer::t_test(x = data_t_test[[2]], n_gems ~ group )
  infer::t_test(x = data_t_test[[3]], n_gems ~ group )


  

# mean_gems_by_groups <- 
# all_data %>% 
#   filter(gempresent == 1) %>% 
#   group_by(uniqueID, round, group) %>% 
#   summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
#   group_by(uniqueID, group) %>% 
#   summarise(n_gems = sum(gem_found)) %>% 
#   group_by(group) %>% 
#   summarise(mean_gems = mean(n_gems))
# 
# 
# 
# all_data %>% 
#   filter(gempresent == 1) %>% 
#   group_by(uniqueID, round, group) %>% 
#   summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
#   group_by(uniqueID, group) %>% 
#   summarise(n_gems = sum(gem_found)) %>% 
#   ggplot() +
#   geom_histogram(aes(x =  n_gems, y =stat(density)), binwidth = 1, fill = "black")+
#   geom_vline(data = mean_gems_by_groups, aes(xintercept = (mean_gems))) +
#   theme_bw(base_size = 20) +
#   labs(x = 'n of environments in which a gem was found') +
#   facet_wrap(~group)
# 

all_data %>% 
  filter(gempresent == 1) %>% 
  group_by(uniqueID, round, group) %>% 
  summarise(gem_found = ifelse(1 %in% gem, 1, 0)) %>% 
  group_by(uniqueID, group) %>% 
  summarise(n_gems = sum(gem_found)) %>% 
  ggplot() +
  geom_boxplot(aes(x =  n_gems/8, y = group, fill = group) ) +
  stat_summary(aes(x =  n_gems/8, y = group, fill = group)) +
  labs(title = 'gem found by group', x = 'proportion of gem found') +
  guides(fill = FALSE)


```

most participants find gems in half of the environments that contain them (4 out 8), and some more than that.

## explore exploit after gem or not

```{r explore exploit, echo=FALSE, message=FALSE, warning=FALSE}

all_data
  group_by(uniqueID, group) %>%
  mutate(exploit = ifelse(lead(choice) == choice, 1, 0),
         explore = ifelse(lead(choice) != choice, 1, 0)) %>%
  mutate(out_cat = case_when(points > 150 ~ 1,
                             points < 0 ~ 3,
                             TRUE ~ 2)) %>% pivot_longer(cols = c(exploit, explore), names_to = "explore_exploit") %>%
  ggplot(aes(
    x = out_cat,
    y = value,
    color = explore_exploit,
    shape = group
  )) +
  stat_summary(size = 1) +
  stat_summary(geom = "line") +
  scale_y_continuous(name = "proportion") +
  scale_x_continuous(
    name = "reward type",
    breaks = c(1, 2, 3),
    labels = c("gem", "no gem", "loss")
  ) +
  #scale_color_brewer(type = 'qual', palette = 6, name = 'explore/exploit')+
  scale_color_manual(values = c("#FFC20A", "#0C7BDC"), name = 'explore/exploit' )+
  theme_bw(15) +
  facet_wrap(~gemlabel)+
  # guides(shape = FALSE)+
  theme(axis.text=element_text(size=20))+
  labs(title = 'explore or exploit by reward type')

# 
#   ggsave(filename = 'explore_exploit.png', explore_exploit, width = 12.5,height=6  )

    
```

## Social behavior


```{r copy by age and demonstrator, echo=FALSE, message=FALSE, warning=FALSE}

all_data %>% 
  filter(!is.na(demo_type)) %>% 
  mutate(social_info_use_num = ifelse(social_info_use == "copy", 1, 0)) %>% 
  group_by(uniqueID, round,group) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  select(unique_rounds, n, demo_type) %>% 
  distinct() %>% 
  group_by(uniqueID,demo_type,group) %>% 
  summarize(mean_copy = mean(n),
            demo_type = demo_type) %>% 
  ggplot() +
  geom_histogram(aes(x=mean_copy, y = stat(density), group = demo_type, fill = demo_type), binwidth = 1) +
  facet_grid(~demo_type+group) +
  labs(title = 'average copy per participant in each treatment') +
  theme_bw(15)


```



```{r points by social info use, echo=FALSE, message=FALSE, warning=FALSE}

points_by_treat <- all_data %>%  
  group_by(unique_rounds) %>% mutate(social_info_use_num = ifelse(social_info_use=="ignore", 0, 1)) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  ggplot()+
  stat_summary(aes(x = n, y = tot_points, color = factor(gem_found, levels = c(1,0)), shape = group)) +
  geom_smooth(aes(x = n, y = tot_points),method = "lm")+
facet_wrap(~demo_type, scales = 'free')+  
  theme_bw(base_size = 15) +
  scale_color_brewer(type = "qual",palette = 2, name = "gem found", label = c("yes", "no"))+
  labs(x = 'n of rounds copying social information', y='total points', title = 'total points by frequency of social info use') +
    theme_bw(15)+
  theme(axis.text=element_text(size=15))

points_by_treat
  

# ggsave(filename = 'points_by_treat.png', points_by_treat, width = 14,height=6  )

```

do adults use more social info?

```{r frequency of copy by round}

all_data %>%
  ggplot() +
  geom_bar(aes(x = factor(trial),  fill = social_info_use), position = "fill")+
  facet_grid(~demo_quality + group)+
  theme()

```



```{r copy frequency by treatment and outcome}

## find the same gem of 

 all_data %>% 
  mutate(social_info_use_num = ifelse(social_info_use == "copy", 1, 0)) %>% 
  group_by(unique_rounds) %>% 
  mutate(n = sum(social_info_use_num)) %>% 
  ungroup() %>% 
  select(uniqueID, n, demo_type, gem_found, group) %>% 
  distinct() %>% 
  group_by(uniqueID,demo_type,group, gem_found) %>% 
#  reframe(mean_copy = mean(n)) %>% 
 # distinct() %>% 
  ggplot() +
  stat_summary(aes(x = demo_type, y = n, color = group)) +
  facet_wrap(~gem_found)


all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
filter(social_info_use == "copy" & gem_found_how != 'alone') %>%
  count(social_info_use) %>%
  ggplot(aes(
    x = demo_quality,
    y = n,
    shape = social_info_use,
    color = group
  )) +
  stat_summary() +
  geom_hline(yintercept = 25 / 64,
             linetype = "dotted",
             color = "red") +
  # facet_wrap(.~group)+
  theme_minimal(14) +
  facet_wrap(. ~ gem_found, labeller = label_both) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))





```

## poisson regression analysis: copy by treatment and demonstrator

```{r differences in social info use by treatment}

## latest version in the plots for the conference presentation

# all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy"  & gempresent ==1) %>%
#   count(social_info_use) %>%
#   ggplot(aes(
#     x = factor(demo_quality),
#     y = n,
#     shape = group,
#     color = demo_quality
#   )) +
#   stat_summary(position = position_dodge(width =.5)) +
#  # geom_hline(yintercept = 25 / 64,
#   #           linetype = "dotted",
#   #          color = "red") +
#   labs(y='average number of copy per round',
#        x= 'treatment (quality of demonstrator)')+
#   scale_color_brewer(
#     type = "qual",
#     palette = 2,
#     name = "demonstrator:",
#     label = c("finds a gem", "settles for a positive option", "explores until the end")
#   ) +
#   scale_x_discrete(labels=c("high", "medium", "low")) +
#  # facet_wrap(.~gem_found) +
#   theme_base(20)
#  # guides(color = FALSE)
# ggsave("plots/social_info_use.png",plot = last_plot(), width = 6, heigh = 6)


# ## difference in copy by group and treatment
# all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy") %>%
#   count(social_info_use) %>% 
#   lmer(n ~ demo_quality * group + (1|uniqueID), data = .) -> c
# 
# summary(c)
# 
# ## condition on gem being present
# all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy" & gempresent == 1 ) %>%
#   count(social_info_use) %>% 
#   lmer(n ~ demo_quality * group + (1|uniqueID), data = .) -> a
# 
# summary(a)



## bayesian models

  model_random_slopes_data <- all_data %>%
  mutate(age_group = group) %>% 
group_by(demo_type, uniqueID, round, age_group, gem_found, age, demo_quality) %>%
  filter(social_info_use == "copy") %>%
  count(social_info_use)

## all copy trials included and random slopes
model_random_slopes <- 
  all_data %>%
  mutate(age_group = group) %>% 
group_by(demo_type, uniqueID, round, age_group, gem_found, age, demo_quality) %>%
  filter(social_info_use == "copy") %>%
  count(social_info_use) %>% 
  brms::brm(n ~ 1 + demo_quality * age_group + (1 + demo_quality | uniqueID), data = ., family = poisson(), iter = 4000) 

plot_model(model_random_slopes)

save(file = paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/poission_regression_all_rounds_slopes.RData'), model_random_slopes)

load(file = paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/poission_regression_all_rounds_slopes.RData'))

# null_brms = update(model_random_slopes, formula = ~ .-demo_quality:group ) 
# 
# # Same but without the interaction term
# BF_brms_bridge = bayes_factor(model_random_slopes, null_brms)
# BF_brms_bridge
# 
# 
# BayesFactor::regressionBF(formula = formula, n ~ 1 + demo_quality * age_group + (1 + demo_quality | uniqueID),  data = model_random_slopes_data)
# ## all copy trials incluformula = # ## all copy trials included
# all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy") %>%
#   count(social_info_use) %>% 
#   brms::brm(n ~ demo_quality * group + (1|uniqueID), data = ., family = poisson(), iter = 3000) -> poission_regression_all_rounds
# 
# 
# save(file = paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/poission_regression_all_rounds.RData'), poission_regression_all_rounds)
# 
# ## other models - not in final version
# all_data %>% group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy" & gempresent == 1 ) %>%
#   count(social_info_use) %>% 
#   brms::brm(n ~ demo_quality * group + (1|uniqueID), data = ., family = poisson(), iter = 3000) -> poission_regression_all_gem_rounds
# 
# poission_regression_all_gem_rounds_copiers <- 
# all_data %>%
#   group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy" & gem_found_how != 'alone') %>%
#   count(social_info_use) %>% 
#   brms::brm(n ~ demo_quality * group + (1 | uniqueID), data = ., family = poisson(), iter = 3000)

# 
# ## freq
# poisson_reg_copy <- 
# all_data %>%
#   group_by(demo_type, uniqueID, round, group, gem_found, age, demo_quality) %>%
#   filter(social_info_use == "copy" & gem_found_how != 'alone') %>%
#   count(social_info_use) %>% 
#   glmer(n ~ demo_quality * group + (1 | uniqueID), data = ., family = poisson())


tab_model(model_random_slopes, pred.labels = 
    c("Intercept",
      "Quality (Medium)",
      "Quality (Worst)",
      "Adults",
      "Quality (Medium) X Adults",
      "Quality (Worst) X Adults"
    ), show.stat = TRUE )

poisson_plot <- 
  plot_model(
  model_random_slopes,
 # axis.lim = c(.2, 2),
  axis.labels = rev(
    c(
      "Quality (Medium)",
      "Quality (Worst)",
      "Adults",
      "Quality (Medium) X Adults",
      "Quality (Worst) X Adults"
    )
  ),
  title = "", vline.color = "grey", vline = 2,show.values = TRUE, 
) +
  ylim(.2,2)+
  theme_base(base_size = 15)+
  theme(plot.background = element_blank())

ggsave("plots/poisson_regression_slopes.png",plot = poisson_plot, width = 6, height = 4)

```

### if and when are gem found


```{r frequency of finding gems by group and demonstrator}

  all_data %>%
  filter(gempresent == 1 )%>%
  ungroup %>%
  group_by(demo_type, gem_found) %>%
  select(uniqueID, round, gem_found, round_gem_found, gempresent, group) %>%
  distinct() %>%
  select(gem_found, round_gem_found) %>%
  summarise(mean_round_found = mean(round_gem_found, na.rm = TRUE),
            n = n()) %>%
  ungroup() %>%
  group_by(demo_type) %>%
  mutate(freq = n / sum(n))


  all_data %>%
  filter(gempresent == 1 )%>%
  ungroup %>%
  group_by(demo_type, gem_found, group) %>%
  select(uniqueID, round, gem_found, round_gem_found, gempresent, group) %>%
  distinct() %>%
  select(gem_found, round_gem_found, group) %>%
  summarise(mean_round_found = mean(round_gem_found, na.rm = TRUE),
            n = n()) %>%
  ungroup() %>%
  group_by(demo_type, group) %>%
  mutate(freq = n / sum(n))


  all_data %>%
  filter(gempresent == 1 )%>%
  ungroup %>%
  group_by(demo_type, gem_found, group) %>%
  select(uniqueID, round, gem_found, round_gem_found, gempresent, group) %>%
  distinct() %>%
  select(gem_found, round_gem_found, group) %>%
  summarise(mean_round_found = mean(round_gem_found, na.rm = TRUE),
            n = n()) %>%
  ungroup() %>%
  group_by(demo_type, group) %>%
  mutate(freq = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(
    x = demo_type,
    y = freq,
    fill = factor(gem_found, levels = c(1,0))
  )) +
  scale_fill_brewer(
    type = "qual",
    palette = 7,
    name = "",
    label = c("yes", "no")
  ) +
  labs(x = 'social information type', title = 'did players find gems?', y = 'proportion of rounds') +
    theme_classic(base_size = 15) +
    theme(axis.text = element_text(size = 10)) +
    facet_wrap( ~ group)
  

  #ggsave(filename = 'gem_found.png', gem_found, width = 8,height=6  )
  
```

```{r gem found when}

hist(all_data$round_gem_found)

all_data %>% 
  filter(gem_found==1 & gem_found_how == 'copier') %>% 
  select(round_gem_found, group, demo_type, uniqueID) %>% 
  group_by(uniqueID) %>% 
  distinct() %>% 
  ggplot(aes(x = group, y = round_gem_found, fill = group)) + 
  geom_half_boxplot()+
  geom_half_point(alpha = 0.1)+
  stat_summary(color = 'red')+
  facet_wrap(~demo_type)

all_data %>% 
  filter(gem_found==1 & gem_found_how == 'copier') %>%
    select(round_gem_found, group, demo_type, uniqueID) %>% 
    group_by(uniqueID) %>% 
distinct() %>% 
  lm(round_gem_found ~ group  , data = .) -> model_when_gem

summary(model_when_gem)
  
```

```{r proportion of copy by repeated staying on a tilew}


data_running_count <- 
all_data %>%
  group_by(round) %>% 
  mutate(running_count_si = sequence(rle(social_info)$lengths)) %>% 
  select(social_info, running_count_si, social_info_use)


base_rates <- all_data %>%
  group_by(round) %>% 
  mutate(running_count_si = sequence(rle(social_info)$lengths)) %>% 
  select(social_info, running_count_si, social_info_use, group) %>% 
  ungroup() %>% 
  group_by(running_count_si, group) %>% 
  summarise(base_rates= n()) 

counts <- all_data %>%
  group_by(round) %>% 
  mutate(running_count_si = sequence(rle(social_info)$lengths)) %>% 
  select(social_info, running_count_si, social_info_use, group) %>% 
  ungroup() %>% 
  group_by(running_count_si, group, social_info_use) %>% 
  summarise(n = n()) 

copy_heuristic <- 
left_join(base_rates, counts, by = c("running_count_si", "group"))%>% 
  mutate(proportion = n/base_rates)

copy_heuristic %>% 
  select(-c(base_rates,n)) %>% 
  filter(social_info_use == "copy") %>% 
  pivot_wider(names_from = c("group"), values_from = "proportion") %>% 
  mutate(difference_copy = adolescents - adults) %>% 
    ggplot() +
  geom_col(aes(x = factor(running_count_si), y = difference_copy, fill = social_info_use),
             position= "stack" ) 

copy_heuristic %>% 
  ggplot() +
  geom_col(aes(x = factor(running_count_si), y = proportion, fill = social_info_use),
             position= "stack" ) +
  facet_wrap(~factor(group))


 

```


