---
title: "Write Reproducible Results Section"
author: "Andrea"
date: "2024-07-31"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

## load packages @andrea implement pck_mgmt script
pacman::p_load(tidyverse,
               rjson,
               data.table,
               gghalves,
               here,
               lme4,
               lmerTest,
               broom.mixed,
               infer,
               ggthemes,
               sjPlot,
               bayestestR)

'%!in%' <- function(x,y)!('%in%'(x,y))

options(scipen = 999,digits = 4)

## function to extract coefficients
source("utils/extract_coefficients.R")

## function to calculate Bayes Factor
source("utils/calculate_BF.R")

## set custom theme
source("https://raw.githubusercontent.com/AndGrad/custom_themes_ggplot/main/theme_plot.R")

```


```{r load data, echo=FALSE, warning=FALSE, message=FALSE }

## demographics dataa
data_demographics <- read_csv(file = paste0(here(), "/data/social/data_social_all_participants_full_sample_demographics"))

## load clen data data
all_data <- read_csv(file = paste0(here(), "/data/social/data_social_all_participants_08-2024.csv"))

all_data <- all_data %>% 
  mutate(demo_quality_f = as.factor(demo_quality),
          age_f = factor(group, levels = c("adults", "adolescents")),
          treatment= factor(
            ifelse(demo_quality_f == "best" & age_f == "adults", "adu_best",
            ifelse(demo_quality_f == "medium" & age_f == "adults", "adu_medium",
            ifelse(demo_quality_f == "worst" & age_f == "adults", "adu_worst",
            ifelse(demo_quality_f == "best" & age_f == "adolescents", "ado_best",
            ifelse(demo_quality_f == "medium" & age_f == "adolescents", "ado_medium",
            ifelse(demo_quality_f == "worst" & age_f == "adolescents", "ado_worst", NA)))))))) ## mutate IVs into factors

```

```{r}

## demographics before excluding participants

## adults gender and age
data_demographics %>% 
    select(group, gender, uniqueID) %>% 
    filter(group=="adults") %>% 
    distinct() %>% 
  group_by(gender) %>% 
  summarise(count = n())


data_demographics %>% 
    select(group, gender, uniqueID, age) %>% 
    filter(group=="adults") %>% 
    distinct() %>% 
    reframe( mean = mean(age, na.rm=TRUE),
               sd = sd(age, na.rm =TRUE),
             range = range(age, na.rm = TRUE))


## adolescents gender and age
data_demographics %>% 
    select(group, gender, uniqueID) %>% 
    filter(group=="adolescents") %>% 
    distinct() %>% 
  group_by(gender) %>% 
  summarise(count = n())


data_demographics %>% 
    select(group, gender, uniqueID, age) %>% 
    filter(group=="adolescents") %>% 
    distinct() %>% 
    reframe( mean = mean(age, na.rm=TRUE),
               sd = sd(age, na.rm =TRUE),
               range = range(age, na.rm = TRUE))


```

```{r}

## demographics after excluding participants

## adults gender and age
all_data %>% 
    select(group, gender, uniqueID) %>% 
    filter(group=="adults") %>% 
    distinct() %>% 
  group_by(gender) %>% 
  summarise(count = n())

all_data %>% 
    select(group, gender, uniqueID, age) %>% 
    filter(group=="adults") %>% 
    distinct() %>% 
      reframe( mean = mean(age, na.rm=TRUE),
               sd = sd(age, na.rm =TRUE),
             range = range(age, na.rm = TRUE))


## adolescents gender and age
all_data %>% 
    select(group, gender, uniqueID) %>% 
    filter(group=="adolescents") %>% 
    distinct() %>% 
  group_by(gender) %>% 
  summarise(count = n())



all_data %>% 
    select(group, uniqueID, age) %>% 
    dplyr::filter(group=="adolescents") %>% 
    distinct() %>%
    reframe( mean = mean(age, na.rm=TRUE),
               sd = sd(age, na.rm =TRUE),
             range = range(age, na.rm = TRUE))


hist(data)

```



## differences in points scored by group

```{r points by age group regression}

## just raw difference in points across conditions
# t_test_points <- all_data %>% 
#   ungroup() %>% 
#   group_by(uniqueID) %>% 
#   mutate(mean_points_player = mean(tot_points, na.rm = TRUE)) %>% 
#   select(mean_points_player, age_f, uniqueID) %>% 
#   distinct() %>% 
#   ungroup() %>% 
#   stats::t.test(mean_points_player ~ age_f, data = ., alternative = "two.sided")

## load model fit object 
base::load(paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/points_age_trial_advisor_model.RData'))

bayestestR::bayesfactor_parameters(points_age_trial_advisor_model,
                                effects = "fixed",
                              
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all", )


table1 <- bayestestR::describe_posterior(points_age_trial_advisor_model, ci = .89, rope_range = c(-.1, .1))
table %>% 
  dplyr::select( -c("ROPE_CI", "ROPE_high", "ROPE_low","Rhat","ESS"))

rope(
  points_age_trial_advisor_model,
  range = c(-0.1, 0.1),
  ci = .89,
  effects = c("fixed"))

  ## parameters of the model
params <- rownames(fixef(points_age_trial_advisor_model))

## names to assign to the params (for covenience when calling results below)
names <- c("intercept", "medium", "low", "adolescents", "ado_medium", "ado_low" )

## extract coefficients from model object 
coef_points <- summarize_model(points_age_trial_advisor_model, params, names)

## list of hypotheses to test  
hyp_list_points <- c(
  "age_fadolescents >  0",
  "demo_quality_fmedium < 0",
  "demo_quality_fworst	 < 0",
  "demo_quality_fmedium:age_fadolescents < 0",
  "demo_quality_fworst:age_fadolescents <  0"
)

## extract BF for each hypothesis
BFs_points <- test_hypotheses(points_age_advisor_model, hyp_list_points)

```

Across all experimental treatments, adolescents and adults did not differ significantly in total number of points scored (two-sided t-test, t = `r round(t_test_points$statistic,2)`, df = `r round(t_test_points$parameter,2)`, p-value = `r round(t_test_points$p.value,2)`). Regression analysis (Figure 3a) shows that the quality of the advisor significantly impacted performance. Both adolescents and adults performed the best in high quality advisor rounds, (β = `r coef_points$intercept$estimate`, C.I.= [`r coef_points$intercept$ci_low`, `r coef_points$intercept$ci_high`])`; while performance declined in the remaining treatments (medium quality: β =`r coef_points$medium$estimate`, C.I.= [`r coef_points$medium$ci_low`,`r coef_points$medium$ci_high`], BF =`r BFs_points[[2]]`; low quality: β =`r coef_points$low$estimate`, C.I.= [`r coef_points$low$ci_low`,`r coef_points$low$ci_high`], BF =`r BFs_points[[3]]`), indicating that worse social information led to fewer points gained. Finally, across all treatments there was no interaction effect between age group and advisor quality (high quality\*adolescents [β =`r coef_points$adolescents$estimate`, C.I. = [`r coef_points$adolescents$ci_low`,`r coef_points$adolescents$ci_high`], BF =`r BFs_points[[1]]`], (medium quality\*adolescents: β =`r coef_points$ado_medium$estimate`, C.I. = [`r coef_points$ado_medium$ci_low`,`r coef_points$ado_medium$ci_high`], BF =`r BFs_points[[4]]`; low quality\*adolescents: β =`r coef_points$ado_low$estimate`, C.I. = [`r coef_points$ado_low$ci_low`,`r coef_points$ado_low$ci_high`], BF =`r BFs_points[[5]]`), suggesting that potential differences in social information use across treatments did not lead to differences in performance.

## Social learning

```{r differences in copy}
## mean copy by group t_test
t_test_copy <- 
  all_data %>%
  group_by(uniqueID, round, gem_found, age_f, demo_quality_f) %>%
  filter(social_info_use == "copy") %>%
  count(social_info_use) %>% 
  ungroup() %>% 
  filter(n != 0) %>% 
  group_by(uniqueID) %>% 
  mutate(mean_copy = mean(n), na.rm = TRUE) %>% 
  select(age_f, uniqueID, mean_copy) %>% 
  distinct() %>% 
  t.test(mean_copy ~ age_f, data = ., alternative = "two.sided")

copy_summary <- all_data %>% 
 group_by(uniqueID, round, gem_found, age_f, demo_quality_f, treatment) %>%
  filter(social_info_use == "copy") %>%
  count(social_info_use) %>% 
  ungroup() %>% 
  filter(n!=0) %>% 
  select(treatment, n ) %>% 
  group_by(treatment) %>% 
  summarise(mean_copy = round(mean(n),2),
             sd = round(sd(n),2))

## load model fit file
load(file = paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/copy_age_advisor_model.RData'))


table2 <- bayestestR::describe_posterior(copy_age_advisor_model, ci = .89, rope_range = c(-.1, .1))
table2 %>% 
  dplyr::select( -c("ROPE_CI", "ROPE_high", "ROPE_low","Rhat","ESS"))


describe_posterior(copy_age_advisor_model,bayesfactor_parameters)

bayesfactor_parameters(points_age_trial_advisor_model)
rstanarm::plot(rope(copy_age_advisor_model))

## parameters of the model
params_copy <- rownames(fixef(copy_age_advisor_model))

## names to assign to the params (for convenience when calling results below)
names_copy <- c("intercept", "medium", "low", "adolescents", "ado_medium", "ado_low" )

## extract coefficients from model object 
coef_copy <- summarize_model(copy_age_advisor_model, params_copy, names_copy, digits = 2)

## list of hypotheses to test  
hyp_list_copy <- c(
  "age_fadolescents >  0",
  "demo_quality_fmedium < 0",
  "demo_quality_fworst	 < 0",
  "demo_quality_fmedium:age_fadolescents < 0",
  "demo_quality_fworst:age_fadolescents <  0"
)

## extract BF for each hypothesis
BFs_copy <- test_hypotheses(copy_age_advisor_model, hyp_list_copy)

## conditional results
conditional_effects(copy_age_advisor_model)

```

Next, we analysed differences in social information use. Across all experimental treatments, adolescents and adults copied advisors with similar frequencies. (two-sided t-test: t = `r round(t_test_copy$statistic,2)`, df = `r round(t_test_copy$parameter,2)`, p = `r round(t_test_copy$p.value,2)`, figure 2b). Interestingly, adolescents copied significantly more than adults in the rounds where the advisors were of high quality (adolescents mean = `r copy_summary$mean_copy[copy_summary$treatment == "ado_best"]`, s.d. =`r copy_summary$sd[copy_summary$treatment == "ado_best"]`; adults mean = `r  copy_summary$mean_copy[copy_summary$treatment == "adu_best"]`, s.d. = `r copy_summary$sd[copy_summary$treatment == "adu_best"]`; IR = `r coef_copy$adolescents$estimate`; CI = [`r coef_copy$adolescents$ci_low`, `r coef_copy$adolescents$ci_high`], BF = `r BFs_copy[[1]]`). In the rest of the experimental treatments there was no difference between adolescents and adults (medium quality\*adolescents: IR = `r coef_copy$ado_medium$estimate`; CI = [`r coef_copy$ado_medium$ci_low`, `r coef_copy$ado_medium$ci_high`], BF = `r BFs_copy[[4]]` ; low quality\*age_group: IR = `r coef_copy$ado_low$estimate`; CI = [`r coef_copy$ado_low$ci_low`, `r coef_copy$ado_low$ci_high`], BF = `r BFs_copy[[5]]`), with both groups copying the medium quality advisor (adolescents mean = `r copy_summary$mean_copy[copy_summary$treatment == "ado_medium"]`, s.d. = `r copy_summary$sd[copy_summary$treatment == "ado_medium"]`; adults mean = `r copy_summary$mean_copy[copy_summary$treatment == "adu_medium"]`, s.d. = `r copy_summary$mean_copy[copy_summary$treatment == "adu_medium"]`; IR = `r coef_copy$medium$estimate`; CI = [`r coef_copy$medium$ci_low`, `r coef_copy$medium$ci_high`], BF \>= `r BFs_copy[[2]]`), and the least when quality of social information was low (adolescents mean = `r copy_summary$mean_copy[copy_summary$treatment == "ado_worst"]`, s.d. = `r copy_summary$sd[copy_summary$treatment == "ado_worst"]`; adults mean = `r copy_summary$mean_copy[copy_summary$treatment == "adu_worst"]`, s.d. = `r copy_summary$sd[copy_summary$treatment == "adu_worst"]`; IR = `r coef_copy$low$estimate`; CI = [`r coef_copy$low$ci_low`, `r coef_copy$low$ci_high`], BF \>= `r BFs_copy[[3]]`). Overall, these results indicate some adaptive social information use in both groups, and especially adolescents, who copied the most in treatments where advisor quality was the highest.

## finding gems

```{r}
## select only one observation per participant
t_test_gem <- all_data %>%  
  filter(gem_found == 1) %>% 
  select(round_gem_found, age_f, demo_quality_f, uniqueID) %>% 
  distinct() %>% 
  ungroup() %>% 
  select(age_f, round_gem_found, demo_quality_f, uniqueID ) %>% 
  group_by(uniqueID) %>% 
  mutate( mean_round_gem_found = mean(round_gem_found),
             sd = sd (round_gem_found)) %>% 
  select(mean_round_gem_found, age_f,uniqueID) %>% 
  distinct() %>% 
  ungroup() %>% 
  stats::t.test(mean_round_gem_found ~ age_f, data = ., alternative = "two.sided")

## mean round gem found by group and social information use 
gem_summary <- all_data %>% 
 filter(gem_found == 1) %>% 
  select(round_gem_found, age_f, demo_quality_f, uniqueID, treatment) %>% 
  distinct() %>% 
  ungroup() %>% 
  select(round_gem_found, treatment ) %>% 
  group_by(treatment) %>% 
   summarise(mean_clicks = round(mean(round_gem_found), 2),
              sd = round(sd(round_gem_found),2))

 ## add information about proportion of gem found
 prop_gem_found <- all_data %>%
   filter(gempresent == 1) %>%
   ungroup %>%
   group_by(treatment, gem_found) %>%
   select(uniqueID, round, gem_found, round_gem_found, gempresent, age_f, treatment) %>%
   distinct() %>%
   select(gem_found, round_gem_found, treatment) %>%
   summarise(mean_round_found = mean(round_gem_found, na.rm = TRUE),
             n = n()) %>%
   ungroup() %>%
   group_by(treatment) %>%
   mutate(freq = round(n / sum(n),2)) %>% 
   filter(gem_found == 1) %>% 
   select(treatment, freq, n) %>% 
   mutate(perc_found = freq*100)
 
## load model fit
# base::load(paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/gem_age_advisor_model.RData'))
base::load(paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/gem_freq_age_advisor_model.RData'))

## parameters of the model
#params_gems <- rownames(fixef(gem_age_advisor_model))
params_gems <- rownames(fixef(gem_freq_age_advisor_model))

## names to assign to the params (for covenience when calling results below)
names_gems <- c("intercept", "medium", "low", "adolescents", "ado_medium", "ado_low" )

## extract coefficients from model object 
coef_gems <- summarize_model(gem_freq_age_advisor_model, params_gems, names_gems, digits = 2)

## list of hypotheses to test  
hyp_list_gems <- c(
  "age_fadolescents <  0",
  "demo_quality_fmedium < 0",
  "demo_quality_fworst	< 0",
  "demo_quality_fmedium:age_fadolescents < 0",
  "demo_quality_fworst:age_fadolescents <  0"
)

plot_model(gem_freq_age_advisor_model)
## extract BF for each hypothesis
BF_gems <- test_hypotheses(gem_freq_age_advisor_model, hyp_list_gems)
```

Finally, we looked at whether differences in social information quality affected the discovery of gems in rounds in which gems were present. Participants were most likely to find gems in high quality advisor rounds (adults: `r prop_gem_found$perc_found[prop_gem_found$treatment == "adu_best"]`%, adolescents: `r prop_gem_found$perc_found[prop_gem_found$treatment == "ado_best"]`%). Results of a multi-level logistic regression indicated that at the difference between groups was not significant (OR = `r coef_gems$adolescents$estimate`, C.I.= [`r coef_gems$adolescents$ci_low`, `r coef_gems$adolescents$ci_high`], BF = `r BF_gems[[1]]`), suggesting that the observed differences in using high quality social information did not lead to differences in how many gems were found found. As expected, both groups were less likely to find gems in the remaining treatments (adults medium quality: `r prop_gem_found$perc_found[prop_gem_found$treatment == "adu_medium"]`%: OR = `r coef_gems$medium$estimate`, C.I.= [`r coef_gems$medium$ci_low`, `r coef_gems$medium$ci_high`], BF = `r BF_gems[[2]]`; adults low quality: `r prop_gem_found$perc_found[prop_gem_found$treatment == "adu_worst"]`%, OR = `r coef_gems$low$estimate`, C.I.= [`r coef_gems$low$ci_low`, `r coef_gems$low$ci_high`], BF = `r BF_gems[[3]]`), indicating that worse social information led to less gems being discovered. In these treatment as well, there was no interaction effect between age group and advisor quality (adolescents medium: `r prop_gem_found$perc_found[prop_gem_found$treatment == "ado_medium"]`%, OR = `r coef_gems$ado_medium$estimate`, C.I. = [`r coef_gems$ado_medium$ci_low`, `r coef_gems$ado_medium$ci_high`], BF = `r BF_gems[[4]]`; adolescents low: `r prop_gem_found$perc_found[prop_gem_found$treatment == "ado_worst"]`%: OR = `r coef_gems$ado_low$estimate`, C.I. = [`r coef_gems$ado_low$ci_low`, `r coef_gems$ado_low$ci_high`], BF = `r BF_gems[[5]]`).

```{r}

base::load(paste0(here(),'/G_Analysis_bevioral_data_social/modelfits/gem_when_age.RData'))

#params_gems <- rownames(fixef(gem_age_advisor_model))
params_gems_when <- rownames(fixef(gem_when_age))

## names to assign to the params (for covenience when calling results below)
names_gems_when <- c("intercept", "adolescents" )

## extract coefficients from model object 
coef_gems_when <- summarize_model(gem_when_age, params_gems_when, names_gems_when, digits = 2)

## list of hypotheses to test  
hyp_list_gems_when <- c(
  "age_fadolescents <  0"
)

## extract BF for each hypothesis
BF_gems_when <- test_hypotheses(gem_when_age, hyp_list_gems_when)


```

To further explore the data, we ran an exploratory regression analysis to test whether in those rounds in which the gem was found exclusively using social information (which adolescents used more often), adolescents were able to find gems earlier than adults. This was not the case (IR = `r coef_gems_when$adolescents$estimate`; CI = [`r coef_gems_when$adolescents$ci_low`, `r coef_gems_when$adolescents$ci_high`], BF = `r BF_gems_when[[1]]`)), indicating that more propensity to copying did not result in earlier finding of gems.

```{r}

#often participants found gems and how many attempts it took them. (adolescents mean clicks = `r gem_summary$mean_clicks[gem_summary$treatment == "ado_best"]`, s.d. = `r gem_summary$sd[gem_summary$treatment == "ado_best"]`; adults mean clicks = `r gem_summary$mean_clicks[gem_summary$treatment == "adu_best"]`, s.d. = `r gem_summary$sd[gem_summary$treatment == "adu_best"]`; two-sided t-test, t = `r round(t_test_gem$statistic, 2)`, df = `r round(t_test_gem$parameter, 2)`, p-value = `r round(t_test_gem$p.value, 2)`). In the high quality advisor rounds (i.e., where the advisor found the gem), adolescents were faster than adults (adolescents mean = `r gem_summary$mean_clicks[gem_summary$treatment == "ado_best"]` clicks, s.d. = `r gem_summary$sd[gem_summary$treatment == "ado_best"]`; adults mean = `r gem_summary$mean_clicks[gem_summary$treatment == "adu_best"]`, s.d. = `r gem_summary$sd[gem_summary$treatment == "adu_best"]`;


#Poisson regression, high quality advisor: IR = `r coef_gems$adolescents$estimate`; CI = [`r coef_gems$adolescents$ci_low`, `r coef_gems$adolescents$ci_high`], BF = `r BF_high_quality`). In the remaining rounds (medium and low quality advisor), participants had to find the gems through individual exploration, resulting in a substantial drop in the proportion of gems found (24%) compared to the high quality advisor rounds (65%). However, when they did find the gems in the medium quality advisor treatment, both adolescents and adults were faster than in the high quality advisor rounds (adolescents mean = `r gem_summary$mean_clicks[gem_summary$treatment == "medium_quality"`, adults mean = `r gem_summary$mean_clicks[gem_summary$treatment == "medium_quality"]`; 


```

```{r}
#Poisson regression, high quality advisor: IR = `r coef_gems$adolescents$estimate`; CI = [`r coef_gems$adolescents$ci_low`, `r coef_gems$adolescents$ci_high`], BF = `r BF_high_quality`). In the remaining rounds (medium and low quality advisor), participants had to find the gems through individual exploration, resulting in a substantial drop in the proportion of gems found (24%) compared to the high quality advisor rounds (65%). However, when they did find the gems in the medium quality advisor treatment, both adolescents and adults were faster than in the high quality advisor rounds (adolescents mean = `r gem_summary$mean_clicks[gem_summary$treatment == "medium_quality"`, adults mean = `r gem_summary$mean_clicks[gem_summary$treatment == "medium_quality"]`; IR = `r coef_gems$medium$estimate`; CI = [`r coef_gems$medium$ci_low`, `r coef_gems$medium$ci_high`], BF = `r BF_medium_quality`), but there was no difference across groups (advisor quality: medium\*age_group: IR = `r coef_gems$ado_medium$estimate`; CI = [`r coef_gems$ado_medium$ci_low`, `r coef_gems$ado_medium$ci_high`], BF = `r BF_ado_medium`). Finally, when participants found gems in the low quality treatment, adolescents were faster than adults (adolescents mean = `r gem_summary$mean_clicks[gem_summary$treatment == "adolescents"]`, adults mean = `r gem_summary$mean_clicks[gem_summary$treatment == "adults"]`; IR = `r coef_gems$low$estimate`; CI = [`r coef_gems$low$ci_low`, `r coef_gems$low$ci_high`], BF = `r BF_low_quality`), but not faster than either group in the high quality advisor rounds (IR = `r coef_gems$ado_low$estimate`; CI = [`r coef_gems$ado_low$ci_low`, `r coef_gems$ado_low$ci_high`]).
         
# Finally, we looked at how often participants found gems and how many attempts it took them. Across all rounds adolescents found gems earlier than adults (adolescents mean clicks = 11.9, s.d. = 6.73; adults mean clicks = 13.1, s.d. = 7.66; two-sided t-test, t = `r round(t_test_gem$statistic,2)`, df = `r round(t_test_gem$parameter,2)`, p-value = `r round(t_test_gem$p.value,2)`). In the high quality advisor rounds (i.e. where the advisor found the gem), adolescents were faster than adults (adolescents mean = 12.8 clicks, s.d. = 5.92; adults mean = 14.1, s.d. = 6.86; poisson regression, high quality advisor: IR = `r coef_gems$adolescents$estimate`; CI = [`r coef_gems$adolescents$ci_low`, `r coef_gems$adolescents$ci_high`], BF = `r BF_high_quality`). In the remaining rounds (medium and low quality advisor), participants had to find the gems through individual exploration, resulting in a substantial drop in proportion of gems found (24%) compared to the high quality advisor rounds (65%). However, when they did find the gems in the medium quality advisor treatment, both adolescents and adults were faster than in the high quality advisor rounds (adolescents mean = 10.4, adults mean = 11.0; IR = `r coef_gems$medium$estimate`; CI = [`r coef_gems$medium$ci_low`, `r coef_gems$medium$ci_high`], BF = `r BF_medium_quality`), but there was no difference across groups (advisor quality:medium\*age_group: IR = `r coef_gems$ado_medium$estimate`; CI = [`r coef_gems$ado_medium$ci_low`, `r coef_gems$ado_medium$ci_high`], BF = `r BF_ado_medium`). Finally, when participants found gems in the low quality treatment, adolescents were faster than adults (adolescents mean = 10.8, adults mean = 12.1; IR = `r coef_gems$low$estimate`; CI = [`r coef_gems$low$ci_low`, `r coef_gems$low$ci_high`], BF = `r BF_low_quality`), but not faster than either group in the high quality advisor rounds (IR = `r coef_gems$ado_low$estimate`; CI = [`r coef_gems$ado_low$ci_low`,  ]                                              
```

coeffcients plot

```{r}

## panel 1
panel_plot1 <- 
  plot_model(
    points_age_advisor_model,
    # axis.lim = c(.2, 2),
    axis.labels = rev(
      c(
        "Quality (Medium)",
        "Quality (Worst)",
        "Adolescents",
        "Quality (Medium) X Adolescents",
        "Quality (Worst) X Adolescents"
      )
    ),
    title = "Points earned (std)", vline.color = "grey", vline = 2,show.values = TRUE, 
  ) +
  labs(tag = "a")+
  theme_base(base_size = 15)+
  theme(plot.background = element_blank(),
        plot.title = element_text(size=15, hjust = 0.5),
        plot.tag.position = c(0,1),
        plot.tag = element_text(hjust = -9)
        )

## panel 2
panel_plot2 <- 
  plot_model(
    copy_age_advisor_model,
    # axis.lim = c(.2, 2),
    axis.labels = rev(
      c(
        "Quality (Medium)",
        "Quality (Worst)",
        "Adolescents",
        "Quality (Medium) X Adolescents",
        "Quality (Worst) X Adolescents"
      )
    ),
    title = "N of copy decisions", 
    vline.color = "grey", vline = 2,
    show.values = TRUE, 
  ) +
  labs(tag = "b")+
  ylim(.2,2)+
  theme_base(base_size = 15)+
  theme(plot.background = element_blank())+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(size=15, hjust = 0.5),
        plot.tag.position = c(0,1),
  )

## panel 3
panel_plot3 <- 
  plot_model(
    gem_freq_age_advisor_model
    ,
    title = "Probabilty to find a gem", 
    vline.color = "grey", vline = 2,show.values = TRUE, 
  ) +
  ylim(0,2.5)+
  labs(tag = "c")+
  theme_base(base_size = 15)+
  theme(plot.background = element_blank()) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(size=15, hjust = 0.5),
        plot.tag.position = c(0,1),
  )


## combine panels
## combine panels
figure3 <- 
  cowplot::plot_grid(
    panel_plot1, panel_plot2, panel_plot3,
   # labels = c("a", "b","c"),
    label_x = -.01,
    #align = "H",
    nrow = 1,
    rel_widths =  c(.95, .65, .65)
  )
figure3

ggsave("plots/figure3.png", figure3, height = 3, width = 10)


```
